---
title: "03_PheWAS.Behavior.Baseline"
output:
  html_document:
    df_print: paged
---

## Install packages #
```{r}
rm(list = ls())
options(stringsAsFactors = FALSE)

library(tidyverse)
library(lme4)
library(lmerTest)
library(FRGEpistasis)
library(viridis)
library(plotrix)
library(PheWAS)
library(ggrepel)
library(effects)
library(fdrtool)
library(reghelper)
library(RColorBrewer)
```

## Load data #
```{r}
load("ABCD.Release.3.0.C4.Merged.Data.PhewasVars.Rda")
```

## Filter data #
```{r}
abcdData_baseline <- abcdData %>% filter(eventname == "baseline_year_1_arm_1")
abcdData_baseline %>% group_by(ethnicity) %>% tally() 

abcdData_baseline_C4 <- abcdData_baseline %>% filter(!is.na(c4a_total))
abcdData_baseline_C4 %>% group_by(ethnicity) %>% tally() 

abcdData_baseline_C4 <- abcdData_baseline_C4 %>% filter(!is.na(pps_y_ss_number))
abcdData_baseline_C4 %>% group_by(ethnicity) %>% tally() 

abcdData_baseline_C4 <- abcdData_baseline_C4 %>% filter(!is.na(pps_y_ss_severity_score))
abcdData_baseline_C4 %>% group_by(ethnicity) %>% tally() 

abcdData_baseline_C4 <- abcdData_baseline_C4 %>% filter(!is.na(Psychosis_wPQ_susp))
abcdData_baseline_C4 %>% group_by(ethnicity) %>% tally() 

abcdData_baseline_C4_filtered <- abcdData_baseline_C4 %>% filter(ethnicity %in% c("AFR", "AMR", "EUR"))
abcdData_baseline_C4_filtered %>% group_by(ethnicity) %>% tally() 

abcdData_baseline_C4_filtered <- abcdData_baseline_C4_filtered %>%
  filter(c4_allele1_structure %in% c("AL","AL-AL","AL-BL", "AL-BS", "BS"))
abcdData_baseline_C4_filtered <- abcdData_baseline_C4_filtered %>%
  filter(c4_allele2_structure %in% c("AL","AL-AL","AL-BL", "AL-BS", "BS"))
```

## Filter to unique family IDs #
```{r}
set.seed(8)

abcdData_baseline_C4_filtered <- abcdData_baseline_C4_filtered %>% 
  group_by(rel_family_id) %>% 
  sample_n(1) 

abcdData_baseline_C4_filtered %>% group_by(rel_family_id) %>% tally() %>% arrange(desc(n))
```

## Coalesce puberty variable #
```{r}
abcdData_baseline_C4_filtered <- 
  abcdData_baseline_C4_filtered %>% 
  mutate(pds_p_ss_all_category_2 = coalesce(pds_p_ss_male_category_2, pds_p_ss_female_category_2)) 
abcdData_baseline_C4_filtered$pds_p_ss_all_category_2 <- as.numeric(abcdData_baseline_C4_filtered$pds_p_ss_all_category_2)
```

## Add 1 to gamma log-link variables that start at 0,  #
```{r}
abcdData_baseline_C4_filtered$bis_y_ss_bas_rr_plus1 <- abcdData_baseline_C4_filtered$bis_y_ss_bas_rr + 1
abcdData_baseline_C4_filtered$bis_y_ss_bas_drive_plus1 <- abcdData_baseline_C4_filtered$bis_y_ss_bas_drive + 1
abcdData_baseline_C4_filtered$pgbi_p_ss_score_plus1 <- abcdData_baseline_C4_filtered$pgbi_p_ss_score + 1
abcdData_baseline_C4_filtered$medhx_ss_4b_p_plus1 <- abcdData_baseline_C4_filtered$medhx_ss_4b_p + 1
abcdData_baseline_C4_filtered$medhx_ss_5b_p_plus1 <- abcdData_baseline_C4_filtered$medhx_ss_5b_p + 1
abcdData_baseline_C4_filtered$medhx_ss_6a_times_p_plus1 <- abcdData_baseline_C4_filtered$medhx_ss_6a_times_p + 1
abcdData_baseline_C4_filtered$medhx_ss_6b_times_p_plus1 <- abcdData_baseline_C4_filtered$medhx_ss_6b_times_p + 1
abcdData_baseline_C4_filtered$medhx_ss_6c_times_p_plus1 <- abcdData_baseline_C4_filtered$medhx_ss_6c_times_p + 1
abcdData_baseline_C4_filtered$medhx_ss_6d_times_p_plus1 <- abcdData_baseline_C4_filtered$medhx_ss_6d_times_p + 1
abcdData_baseline_C4_filtered$medhx_ss_6e_times_p_plus1 <- abcdData_baseline_C4_filtered$medhx_ss_6e_times_p + 1
abcdData_baseline_C4_filtered$medhx_ss_6f_times_p_plus1 <- abcdData_baseline_C4_filtered$medhx_ss_6f_times_p + 1
abcdData_baseline_C4_filtered$medhx_ss_6g_times_p_plus1 <- abcdData_baseline_C4_filtered$medhx_ss_6g_times_p + 1
abcdData_baseline_C4_filtered$medhx_ss_6h_times_p_plus1 <- abcdData_baseline_C4_filtered$medhx_ss_6h_times_p + 1
abcdData_baseline_C4_filtered$medhx_ss_6i_times_p_plus1 <- abcdData_baseline_C4_filtered$medhx_ss_6i_times_p + 1
abcdData_baseline_C4_filtered$medhx_ss_6j_times_p_plus1 <- abcdData_baseline_C4_filtered$medhx_ss_6j_times_p + 1
abcdData_baseline_C4_filtered$medhx_ss_6k_times_p_plus1 <- abcdData_baseline_C4_filtered$medhx_ss_6k_times_p + 1
abcdData_baseline_C4_filtered$medhx_ss_6l_times_p_plus1 <- abcdData_baseline_C4_filtered$medhx_ss_6l_times_p + 1
abcdData_baseline_C4_filtered$medhx_ss_6m_times_p_plus1 <- abcdData_baseline_C4_filtered$medhx_ss_6m_times_p + 1
abcdData_baseline_C4_filtered$medhx_ss_6n_times_p_plus1 <- abcdData_baseline_C4_filtered$medhx_ss_6n_times_p + 1
abcdData_baseline_C4_filtered$medhx_ss_6o_times_p_plus1 <- abcdData_baseline_C4_filtered$medhx_ss_6o_times_p + 1
abcdData_baseline_C4_filtered$medhx_ss_6p_times_p_plus1 <- abcdData_baseline_C4_filtered$medhx_ss_6p_times_p + 1
abcdData_baseline_C4_filtered$medhx_ss_6q_times_p_plus1 <- abcdData_baseline_C4_filtered$medhx_ss_6q_times_p + 1
abcdData_baseline_C4_filtered$medhx_ss_6r_times_p_plus1 <- abcdData_baseline_C4_filtered$medhx_ss_6r_times_p + 1
abcdData_baseline_C4_filtered$medhx_ss_6s_times_p_plus1 <- abcdData_baseline_C4_filtered$medhx_ss_6s_times_p + 1
abcdData_baseline_C4_filtered$medhx_ss_9b_p_plus1 <- abcdData_baseline_C4_filtered$medhx_ss_9b_p + 1
abcdData_baseline_C4_filtered$devhx_16_p_plus1 <- abcdData_baseline_C4_filtered$devhx_16_p + 1
abcdData_baseline_C4_filtered$bis_y_ss_basm_rr_plus1 <- abcdData_baseline_C4_filtered$bis_y_ss_basm_rr + 1
abcdData_baseline_C4_filtered$bis_y_ss_basm_drive_plus1 <- abcdData_baseline_C4_filtered$bis_y_ss_basm_drive + 1
abcdData_baseline_C4_filtered$bis_y_ss_bas_fs_plus1 <- abcdData_baseline_C4_filtered$bis_y_ss_bas_fs + 1
abcdData_baseline_C4_filtered$resiliency5a_y_plus1 <- abcdData_baseline_C4_filtered$resiliency5a_y + 1
abcdData_baseline_C4_filtered$resiliency6a_y_plus1 <- abcdData_baseline_C4_filtered$resiliency6a_y + 1
abcdData_baseline_C4_filtered$resiliency5b_y_plus1 <- abcdData_baseline_C4_filtered$resiliency5b_y + 1
abcdData_baseline_C4_filtered$resiliency6b_y_plus1 <- abcdData_baseline_C4_filtered$resiliency6b_y + 1
abcdData_baseline_C4_filtered$fes_p_ss_fc_pr_plus1 <- abcdData_baseline_C4_filtered$fes_p_ss_fc_pr + 1
abcdData_baseline_C4_filtered$psb_p_ss_mean_plus1 <- abcdData_baseline_C4_filtered$psb_p_ss_mean + 1
abcdData_baseline_C4_filtered$fes_y_ss_fc_pr_plus1 <- abcdData_baseline_C4_filtered$fes_y_ss_fc_pr + 1
abcdData_baseline_C4_filtered$psb_y_ss_mean_plus1 <- abcdData_baseline_C4_filtered$psb_y_ss_mean + 1
abcdData_baseline_C4_filtered$srpf_y_ss_iiss_plus1 <- abcdData_baseline_C4_filtered$srpf_y_ss_iiss + 1
abcdData_baseline_C4_filtered$stq_y_ss_weekday_plus1 <- abcdData_baseline_C4_filtered$stq_y_ss_weekday + 1
abcdData_baseline_C4_filtered$stq_y_ss_weekend_plus1 <- abcdData_baseline_C4_filtered$stq_y_ss_weekend + 1
```

## Update labels #
```{r}
abcdData_baseline_C4_filtered$ethnicity <- as.factor(abcdData_baseline_C4_filtered$ethnicity)
levels(abcdData_baseline_C4_filtered$ethnicity)
levels(abcdData_baseline_C4_filtered$ethnicity) <- list (Latinx = "AMR", EUR = "EUR", AFR = "AFR")
levels(abcdData_baseline_C4_filtered$ethnicity)
```

## Group by ancestry and sex #
```{r}
afr <- filter(abcdData_baseline_C4_filtered, ethnicity == "AFR")
latinx <- filter(abcdData_baseline_C4_filtered, ethnicity == "Latinx")
eur <- filter(abcdData_baseline_C4_filtered, ethnicity == "EUR")

male <- filter(abcdData_baseline_C4_filtered, sex == "M")
female <- filter(abcdData_baseline_C4_filtered, sex == "F")
```

## Check distribution of psychosis score #
```{r}
# Number of symptoms
my.plot <- ggplot(abcdData_baseline_C4_filtered, aes(x=abcdData_baseline_C4_filtered$pps_y_ss_number)) +
    geom_histogram(fill="#69b3a2", color="#e9ecef", alpha=0.6) + 
    labs(x="PQ-B Symptoms", y = "Count") +
    theme_classic()
my.plot

my.plot <- ggplot(abcdData_baseline_C4_filtered, aes(x=abcdData_baseline_C4_filtered$pps_y_ss_number, fill=ethnicity)) +
    geom_histogram(color="black", alpha=0.6) + 
    labs(x="Prodromal Questionnaire - Brief: Number of Events", y = "Count", fill = "Ancestry") +
  theme_classic()
myplot1 <- my.plot + facet_grid(~ethnicity) + theme(legend.position="none")
myplot1
ggsave(myplot1, file = '../results/Figure1_Count_PQBnumber.Ancestry.pdf', device = cairo_pdf, width = 6, height=2, units = 'in')

# Severity of symptoms
my.plot <- ggplot(abcdData_baseline_C4_filtered, aes(x=abcdData_baseline_C4_filtered$pps_y_ss_severity_score)) +
    geom_histogram(fill="#69b3a2", color="#e9ecef", alpha=0.6) + 
    labs(x="PQ-B Severity", y = "Count") +
    theme_classic()
my.plot

my.plot <- ggplot(abcdData_baseline_C4_filtered, aes(x=abcdData_baseline_C4_filtered$pps_y_ss_severity_score, fill=ethnicity)) +
    geom_histogram(color="black", alpha=0.6) + 
    labs(x="Prodromal Questionnaire - Brief: Severity of Events", y = "Count", fill = "Ancestry") +
  theme_classic()
myplot1 <- my.plot + facet_grid(~ethnicity) + theme(legend.position="none")
myplot1
ggsave(myplot1, file = '../results/Figure1_Count_PQBseverity.Ancestry.pdf', device = cairo_pdf, width = 6, height=2, units = 'in')

# Binary score
my.plot <- ggplot(abcdData_baseline_C4_filtered, aes(x=abcdData_baseline_C4_filtered$Psychosis_wPQ_susp)) +
    geom_histogram(fill="#69b3a2", color="#e9ecef", alpha=0.6, stat="count") + 
    labs(x="Prodromal Psychosis Binary Score", y = "Count") +
    theme_classic()
my.plot

my.plot <- ggplot(abcdData_baseline_C4_filtered, aes(x=abcdData_baseline_C4_filtered$Psychosis_wPQ_susp, fill=ethnicity)) +
    geom_histogram(color="black", alpha=0.6, stat="count") + 
    labs(x="Prodromal Psychosis Binary Score", y = "Count", fill = "Ancestry") +
  theme_classic()
myplot1 <- my.plot + facet_grid(~ethnicity) + theme(legend.position="none")
myplot1
ggsave(myplot1, file = '../results/Figure1_Count_BinaryPsychosis.Ancestry.pdf', device = cairo_pdf, width = 6, height=2, units = 'in')
```

## Tally binary score #
```{r}
abcdData_baseline_C4_filtered %>% group_by(Psychosis_wPQ_susp) %>% tally()
```

## Rename phenotypes for PheWAS plotting #
```{r}
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'bis_y_ss_bas_rr_plus1'] <- 'bis_y_ss_bas_rr'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'bis_y_ss_bas_drive_plus1'] <- 'bis_y_ss_bas_drive'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'pgbi_p_ss_score_plus1'] <- 'pgbi_p_ss_score'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'medhx_ss_4b_p_plus1'] <- 'medhx_ss_4b_p'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'medhx_ss_5b_p_plus1'] <- 'medhx_ss_5b_p'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'medhx_ss_6a_times_p_plus1'] <- 'medhx_ss_6a_times_p'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'medhx_ss_6b_times_p_plus1'] <- 'medhx_ss_6b_times_p'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'medhx_ss_6c_times_p_plus1'] <- 'medhx_ss_6c_times_p'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'medhx_ss_6d_times_p_plus1'] <- 'medhx_ss_6d_times_p'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'medhx_ss_6e_times_p_plus1'] <- 'medhx_ss_6e_times_p'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'medhx_ss_6f_times_p_plus1'] <- 'medhx_ss_6f_times_p'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'medhx_ss_6g_times_p_plus1'] <- 'medhx_ss_6g_times_p'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'medhx_ss_6h_times_p_plus1'] <- 'medhx_ss_6h_times_p'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'medhx_ss_6i_times_p_plus1'] <- 'medhx_ss_6i_times_p'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'medhx_ss_6j_times_p_plus1'] <- 'medhx_ss_6j_times_p'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'medhx_ss_6k_times_p_plus1'] <- 'medhx_ss_6k_times_p'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'medhx_ss_6l_times_p_plus1'] <- 'medhx_ss_6l_times_p'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'medhx_ss_6m_times_p_plus1'] <- 'medhx_ss_6m_times_p'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'medhx_ss_6n_times_p_plus1'] <- 'medhx_ss_6n_times_p'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'medhx_ss_6o_times_p_plus1'] <- 'medhx_ss_6o_times_p'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'medhx_ss_6p_times_p_plus1'] <- 'medhx_ss_6p_times_p'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'medhx_ss_6q_times_p_plus1'] <- 'medhx_ss_6q_times_p'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'medhx_ss_6r_times_p_plus1'] <- 'medhx_ss_6r_times_p'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'medhx_ss_6s_times_p_plus1'] <- 'medhx_ss_6s_times_p'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'medhx_ss_9b_p_plus1'] <- 'medhx_ss_9b_p'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'devhx_16_p_plus1'] <- 'devhx_16_p'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'bis_y_ss_basm_rr_plus1'] <- 'bis_y_ss_basm_rr'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'bis_y_ss_basm_drive_plus1'] <- 'bis_y_ss_basm_drive'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'bis_y_ss_bas_fs_plus1'] <- 'bis_y_ss_bas_fs'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'resiliency5a_y_plus1'] <- 'resiliency5a_y_p'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'resiliency6a_y_plus1'] <- 'resiliency6a_y_p'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'resiliency5b_y_plus1'] <- 'resiliency5b_y_p'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'resiliency6b_y_plus1'] <- 'resiliency6b_y_p'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'fes_p_ss_fc_pr_plus1'] <- 'fes_p_ss_fc_pr_p'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'psb_p_ss_mean_plus1'] <- 'psb_p_ss_mean'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'fes_y_ss_fc_pr_plus1'] <- 'fes_y_ss_fc_pr'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'psb_y_ss_mean_plus1'] <- 'psb_y_ss_mean'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'srpf_y_ss_iiss_plus1'] <- 'srpf_y_ss_iiss'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'stq_y_ss_weekday_plus1'] <- 'stq_y_ss_weekday'
names(abcdData_baseline_C4_filtered)[names(abcdData_baseline_C4_filtered) == 'stq_y_ss_weekend_plus1'] <- 'stq_y_ss_weekend'

names(afr)[names(afr) == 'bis_y_ss_bas_rr_plus1'] <- 'bis_y_ss_bas_rr'
names(afr)[names(afr) == 'bis_y_ss_bas_drive_plus1'] <- 'bis_y_ss_bas_drive'
names(afr)[names(afr) == 'pgbi_p_ss_score_plus1'] <- 'pgbi_p_ss_score'
names(afr)[names(afr) == 'medhx_ss_4b_p_plus1'] <- 'medhx_ss_4b_p'
names(afr)[names(afr) == 'medhx_ss_5b_p_plus1'] <- 'medhx_ss_5b_p'
names(afr)[names(afr) == 'medhx_ss_6a_times_p_plus1'] <- 'medhx_ss_6a_times_p'
names(afr)[names(afr) == 'medhx_ss_6b_times_p_plus1'] <- 'medhx_ss_6b_times_p'
names(afr)[names(afr) == 'medhx_ss_6c_times_p_plus1'] <- 'medhx_ss_6c_times_p'
names(afr)[names(afr) == 'medhx_ss_6d_times_p_plus1'] <- 'medhx_ss_6d_times_p'
names(afr)[names(afr) == 'medhx_ss_6e_times_p_plus1'] <- 'medhx_ss_6e_times_p'
names(afr)[names(afr) == 'medhx_ss_6f_times_p_plus1'] <- 'medhx_ss_6f_times_p'
names(afr)[names(afr) == 'medhx_ss_6g_times_p_plus1'] <- 'medhx_ss_6g_times_p'
names(afr)[names(afr) == 'medhx_ss_6h_times_p_plus1'] <- 'medhx_ss_6h_times_p'
names(afr)[names(afr) == 'medhx_ss_6i_times_p_plus1'] <- 'medhx_ss_6i_times_p'
names(afr)[names(afr) == 'medhx_ss_6j_times_p_plus1'] <- 'medhx_ss_6j_times_p'
names(afr)[names(afr) == 'medhx_ss_6k_times_p_plus1'] <- 'medhx_ss_6k_times_p'
names(afr)[names(afr) == 'medhx_ss_6l_times_p_plus1'] <- 'medhx_ss_6l_times_p'
names(afr)[names(afr) == 'medhx_ss_6m_times_p_plus1'] <- 'medhx_ss_6m_times_p'
names(afr)[names(afr) == 'medhx_ss_6n_times_p_plus1'] <- 'medhx_ss_6n_times_p'
names(afr)[names(afr) == 'medhx_ss_6o_times_p_plus1'] <- 'medhx_ss_6o_times_p'
names(afr)[names(afr) == 'medhx_ss_6p_times_p_plus1'] <- 'medhx_ss_6p_times_p'
names(afr)[names(afr) == 'medhx_ss_6q_times_p_plus1'] <- 'medhx_ss_6q_times_p'
names(afr)[names(afr) == 'medhx_ss_6r_times_p_plus1'] <- 'medhx_ss_6r_times_p'
names(afr)[names(afr) == 'medhx_ss_6s_times_p_plus1'] <- 'medhx_ss_6s_times_p'
names(afr)[names(afr) == 'medhx_ss_9b_p_plus1'] <- 'medhx_ss_9b_p'
names(afr)[names(afr) == 'devhx_16_p_plus1'] <- 'devhx_16_p'
names(afr)[names(afr) == 'bis_y_ss_basm_rr_plus1'] <- 'bis_y_ss_basm_rr'
names(afr)[names(afr) == 'bis_y_ss_basm_drive_plus1'] <- 'bis_y_ss_basm_drive'
names(afr)[names(afr) == 'bis_y_ss_bas_fs_plus1'] <- 'bis_y_ss_bas_fs'
names(afr)[names(afr) == 'resiliency5a_y_plus1'] <- 'resiliency5a_y_p'
names(afr)[names(afr) == 'resiliency6a_y_plus1'] <- 'resiliency6a_y_p'
names(afr)[names(afr) == 'resiliency5b_y_plus1'] <- 'resiliency5b_y_p'
names(afr)[names(afr) == 'resiliency6b_y_plus1'] <- 'resiliency6b_y_p'
names(afr)[names(afr) == 'fes_p_ss_fc_pr_plus1'] <- 'fes_p_ss_fc_pr_p'
names(afr)[names(afr) == 'psb_p_ss_mean_plus1'] <- 'psb_p_ss_mean'
names(afr)[names(afr) == 'fes_y_ss_fc_pr_plus1'] <- 'fes_y_ss_fc_pr'
names(afr)[names(afr) == 'psb_y_ss_mean_plus1'] <- 'psb_y_ss_mean'
names(afr)[names(afr) == 'srpf_y_ss_iiss_plus1'] <- 'srpf_y_ss_iiss'
names(afr)[names(afr) == 'stq_y_ss_weekday_plus1'] <- 'stq_y_ss_weekday'
names(afr)[names(afr) == 'stq_y_ss_weekend_plus1'] <- 'stq_y_ss_weekend'

names(latinx)[names(latinx) == 'bis_y_ss_bas_rr_plus1'] <- 'bis_y_ss_bas_rr'
names(latinx)[names(latinx) == 'bis_y_ss_bas_drive_plus1'] <- 'bis_y_ss_bas_drive'
names(latinx)[names(latinx) == 'pgbi_p_ss_score_plus1'] <- 'pgbi_p_ss_score'
names(latinx)[names(latinx) == 'medhx_ss_4b_p_plus1'] <- 'medhx_ss_4b_p'
names(latinx)[names(latinx) == 'medhx_ss_5b_p_plus1'] <- 'medhx_ss_5b_p'
names(latinx)[names(latinx) == 'medhx_ss_6a_times_p_plus1'] <- 'medhx_ss_6a_times_p'
names(latinx)[names(latinx) == 'medhx_ss_6b_times_p_plus1'] <- 'medhx_ss_6b_times_p'
names(latinx)[names(latinx) == 'medhx_ss_6c_times_p_plus1'] <- 'medhx_ss_6c_times_p'
names(latinx)[names(latinx) == 'medhx_ss_6d_times_p_plus1'] <- 'medhx_ss_6d_times_p'
names(latinx)[names(latinx) == 'medhx_ss_6e_times_p_plus1'] <- 'medhx_ss_6e_times_p'
names(latinx)[names(latinx) == 'medhx_ss_6f_times_p_plus1'] <- 'medhx_ss_6f_times_p'
names(latinx)[names(latinx) == 'medhx_ss_6g_times_p_plus1'] <- 'medhx_ss_6g_times_p'
names(latinx)[names(latinx) == 'medhx_ss_6h_times_p_plus1'] <- 'medhx_ss_6h_times_p'
names(latinx)[names(latinx) == 'medhx_ss_6i_times_p_plus1'] <- 'medhx_ss_6i_times_p'
names(latinx)[names(latinx) == 'medhx_ss_6j_times_p_plus1'] <- 'medhx_ss_6j_times_p'
names(latinx)[names(latinx) == 'medhx_ss_6k_times_p_plus1'] <- 'medhx_ss_6k_times_p'
names(latinx)[names(latinx) == 'medhx_ss_6l_times_p_plus1'] <- 'medhx_ss_6l_times_p'
names(latinx)[names(latinx) == 'medhx_ss_6m_times_p_plus1'] <- 'medhx_ss_6m_times_p'
names(latinx)[names(latinx) == 'medhx_ss_6n_times_p_plus1'] <- 'medhx_ss_6n_times_p'
names(latinx)[names(latinx) == 'medhx_ss_6o_times_p_plus1'] <- 'medhx_ss_6o_times_p'
names(latinx)[names(latinx) == 'medhx_ss_6p_times_p_plus1'] <- 'medhx_ss_6p_times_p'
names(latinx)[names(latinx) == 'medhx_ss_6q_times_p_plus1'] <- 'medhx_ss_6q_times_p'
names(latinx)[names(latinx) == 'medhx_ss_6r_times_p_plus1'] <- 'medhx_ss_6r_times_p'
names(latinx)[names(latinx) == 'medhx_ss_6s_times_p_plus1'] <- 'medhx_ss_6s_times_p'
names(latinx)[names(latinx) == 'medhx_ss_9b_p_plus1'] <- 'medhx_ss_9b_p'
names(latinx)[names(latinx) == 'devhx_16_p_plus1'] <- 'devhx_16_p'
names(latinx)[names(latinx) == 'bis_y_ss_basm_rr_plus1'] <- 'bis_y_ss_basm_rr'
names(latinx)[names(latinx) == 'bis_y_ss_basm_drive_plus1'] <- 'bis_y_ss_basm_drive'
names(latinx)[names(latinx) == 'bis_y_ss_bas_fs_plus1'] <- 'bis_y_ss_bas_fs'
names(latinx)[names(latinx) == 'resiliency5a_y_plus1'] <- 'resiliency5a_y_p'
names(latinx)[names(latinx) == 'resiliency6a_y_plus1'] <- 'resiliency6a_y_p'
names(latinx)[names(latinx) == 'resiliency5b_y_plus1'] <- 'resiliency5b_y_p'
names(latinx)[names(latinx) == 'resiliency6b_y_plus1'] <- 'resiliency6b_y_p'
names(latinx)[names(latinx) == 'fes_p_ss_fc_pr_plus1'] <- 'fes_p_ss_fc_pr_p'
names(latinx)[names(latinx) == 'psb_p_ss_mean_plus1'] <- 'psb_p_ss_mean'
names(latinx)[names(latinx) == 'fes_y_ss_fc_pr_plus1'] <- 'fes_y_ss_fc_pr'
names(latinx)[names(latinx) == 'psb_y_ss_mean_plus1'] <- 'psb_y_ss_mean'
names(latinx)[names(latinx) == 'srpf_y_ss_iiss_plus1'] <- 'srpf_y_ss_iiss'
names(latinx)[names(latinx) == 'stq_y_ss_weekday_plus1'] <- 'stq_y_ss_weekday'
names(latinx)[names(latinx) == 'stq_y_ss_weekend_plus1'] <- 'stq_y_ss_weekend'

names(eur)[names(eur) == 'bis_y_ss_bas_rr_plus1'] <- 'bis_y_ss_bas_rr'
names(eur)[names(eur) == 'bis_y_ss_bas_drive_plus1'] <- 'bis_y_ss_bas_drive'
names(eur)[names(eur) == 'pgbi_p_ss_score_plus1'] <- 'pgbi_p_ss_score'
names(eur)[names(eur) == 'medhx_ss_4b_p_plus1'] <- 'medhx_ss_4b_p'
names(eur)[names(eur) == 'medhx_ss_5b_p_plus1'] <- 'medhx_ss_5b_p'
names(eur)[names(eur) == 'medhx_ss_6a_times_p_plus1'] <- 'medhx_ss_6a_times_p'
names(eur)[names(eur) == 'medhx_ss_6b_times_p_plus1'] <- 'medhx_ss_6b_times_p'
names(eur)[names(eur) == 'medhx_ss_6c_times_p_plus1'] <- 'medhx_ss_6c_times_p'
names(eur)[names(eur) == 'medhx_ss_6d_times_p_plus1'] <- 'medhx_ss_6d_times_p'
names(eur)[names(eur) == 'medhx_ss_6e_times_p_plus1'] <- 'medhx_ss_6e_times_p'
names(eur)[names(eur) == 'medhx_ss_6f_times_p_plus1'] <- 'medhx_ss_6f_times_p'
names(eur)[names(eur) == 'medhx_ss_6g_times_p_plus1'] <- 'medhx_ss_6g_times_p'
names(eur)[names(eur) == 'medhx_ss_6h_times_p_plus1'] <- 'medhx_ss_6h_times_p'
names(eur)[names(eur) == 'medhx_ss_6i_times_p_plus1'] <- 'medhx_ss_6i_times_p'
names(eur)[names(eur) == 'medhx_ss_6j_times_p_plus1'] <- 'medhx_ss_6j_times_p'
names(eur)[names(eur) == 'medhx_ss_6k_times_p_plus1'] <- 'medhx_ss_6k_times_p'
names(eur)[names(eur) == 'medhx_ss_6l_times_p_plus1'] <- 'medhx_ss_6l_times_p'
names(eur)[names(eur) == 'medhx_ss_6m_times_p_plus1'] <- 'medhx_ss_6m_times_p'
names(eur)[names(eur) == 'medhx_ss_6n_times_p_plus1'] <- 'medhx_ss_6n_times_p'
names(eur)[names(eur) == 'medhx_ss_6o_times_p_plus1'] <- 'medhx_ss_6o_times_p'
names(eur)[names(eur) == 'medhx_ss_6p_times_p_plus1'] <- 'medhx_ss_6p_times_p'
names(eur)[names(eur) == 'medhx_ss_6q_times_p_plus1'] <- 'medhx_ss_6q_times_p'
names(eur)[names(eur) == 'medhx_ss_6r_times_p_plus1'] <- 'medhx_ss_6r_times_p'
names(eur)[names(eur) == 'medhx_ss_6s_times_p_plus1'] <- 'medhx_ss_6s_times_p'
names(eur)[names(eur) == 'medhx_ss_9b_p_plus1'] <- 'medhx_ss_9b_p'
names(eur)[names(eur) == 'devhx_16_p_plus1'] <- 'devhx_16_p'
names(eur)[names(eur) == 'bis_y_ss_basm_rr_plus1'] <- 'bis_y_ss_basm_rr'
names(eur)[names(eur) == 'bis_y_ss_basm_drive_plus1'] <- 'bis_y_ss_basm_drive'
names(eur)[names(eur) == 'bis_y_ss_bas_fs_plus1'] <- 'bis_y_ss_bas_fs'
names(eur)[names(eur) == 'resiliency5a_y_plus1'] <- 'resiliency5a_y_p'
names(eur)[names(eur) == 'resiliency6a_y_plus1'] <- 'resiliency6a_y_p'
names(eur)[names(eur) == 'resiliency5b_y_plus1'] <- 'resiliency5b_y_p'
names(eur)[names(eur) == 'resiliency6b_y_plus1'] <- 'resiliency6b_y_p'
names(eur)[names(eur) == 'fes_p_ss_fc_pr_plus1'] <- 'fes_p_ss_fc_pr_p'
names(eur)[names(eur) == 'psb_p_ss_mean_plus1'] <- 'psb_p_ss_mean'
names(eur)[names(eur) == 'fes_y_ss_fc_pr_plus1'] <- 'fes_y_ss_fc_pr'
names(eur)[names(eur) == 'psb_y_ss_mean_plus1'] <- 'psb_y_ss_mean'
names(eur)[names(eur) == 'srpf_y_ss_iiss_plus1'] <- 'srpf_y_ss_iiss'
names(eur)[names(eur) == 'stq_y_ss_weekday_plus1'] <- 'stq_y_ss_weekday'
names(eur)[names(eur) == 'stq_y_ss_weekend_plus1'] <- 'stq_y_ss_weekend'

names(female)[names(female) == 'bis_y_ss_bas_rr_plus1'] <- 'bis_y_ss_bas_rr'
names(female)[names(female) == 'bis_y_ss_bas_drive_plus1'] <- 'bis_y_ss_bas_drive'
names(female)[names(female) == 'pgbi_p_ss_score_plus1'] <- 'pgbi_p_ss_score'
names(female)[names(female) == 'medhx_ss_4b_p_plus1'] <- 'medhx_ss_4b_p'
names(female)[names(female) == 'medhx_ss_5b_p_plus1'] <- 'medhx_ss_5b_p'
names(female)[names(female) == 'medhx_ss_6a_times_p_plus1'] <- 'medhx_ss_6a_times_p'
names(female)[names(female) == 'medhx_ss_6b_times_p_plus1'] <- 'medhx_ss_6b_times_p'
names(female)[names(female) == 'medhx_ss_6c_times_p_plus1'] <- 'medhx_ss_6c_times_p'
names(female)[names(female) == 'medhx_ss_6d_times_p_plus1'] <- 'medhx_ss_6d_times_p'
names(female)[names(female) == 'medhx_ss_6e_times_p_plus1'] <- 'medhx_ss_6e_times_p'
names(female)[names(female) == 'medhx_ss_6f_times_p_plus1'] <- 'medhx_ss_6f_times_p'
names(female)[names(female) == 'medhx_ss_6g_times_p_plus1'] <- 'medhx_ss_6g_times_p'
names(female)[names(female) == 'medhx_ss_6h_times_p_plus1'] <- 'medhx_ss_6h_times_p'
names(female)[names(female) == 'medhx_ss_6i_times_p_plus1'] <- 'medhx_ss_6i_times_p'
names(female)[names(female) == 'medhx_ss_6j_times_p_plus1'] <- 'medhx_ss_6j_times_p'
names(female)[names(female) == 'medhx_ss_6k_times_p_plus1'] <- 'medhx_ss_6k_times_p'
names(female)[names(female) == 'medhx_ss_6l_times_p_plus1'] <- 'medhx_ss_6l_times_p'
names(female)[names(female) == 'medhx_ss_6m_times_p_plus1'] <- 'medhx_ss_6m_times_p'
names(female)[names(female) == 'medhx_ss_6n_times_p_plus1'] <- 'medhx_ss_6n_times_p'
names(female)[names(female) == 'medhx_ss_6o_times_p_plus1'] <- 'medhx_ss_6o_times_p'
names(female)[names(female) == 'medhx_ss_6p_times_p_plus1'] <- 'medhx_ss_6p_times_p'
names(female)[names(female) == 'medhx_ss_6q_times_p_plus1'] <- 'medhx_ss_6q_times_p'
names(female)[names(female) == 'medhx_ss_6r_times_p_plus1'] <- 'medhx_ss_6r_times_p'
names(female)[names(female) == 'medhx_ss_6s_times_p_plus1'] <- 'medhx_ss_6s_times_p'
names(female)[names(female) == 'medhx_ss_9b_p_plus1'] <- 'medhx_ss_9b_p'
names(female)[names(female) == 'devhx_16_p_plus1'] <- 'devhx_16_p'
names(female)[names(female) == 'bis_y_ss_basm_rr_plus1'] <- 'bis_y_ss_basm_rr'
names(female)[names(female) == 'bis_y_ss_basm_drive_plus1'] <- 'bis_y_ss_basm_drive'
names(female)[names(female) == 'bis_y_ss_bas_fs_plus1'] <- 'bis_y_ss_bas_fs'
names(female)[names(female) == 'resiliency5a_y_plus1'] <- 'resiliency5a_y_p'
names(female)[names(female) == 'resiliency6a_y_plus1'] <- 'resiliency6a_y_p'
names(female)[names(female) == 'resiliency5b_y_plus1'] <- 'resiliency5b_y_p'
names(female)[names(female) == 'resiliency6b_y_plus1'] <- 'resiliency6b_y_p'
names(female)[names(female) == 'fes_p_ss_fc_pr_plus1'] <- 'fes_p_ss_fc_pr_p'
names(female)[names(female) == 'psb_p_ss_mean_plus1'] <- 'psb_p_ss_mean'
names(female)[names(female) == 'fes_y_ss_fc_pr_plus1'] <- 'fes_y_ss_fc_pr'
names(female)[names(female) == 'psb_y_ss_mean_plus1'] <- 'psb_y_ss_mean'
names(female)[names(female) == 'srpf_y_ss_iiss_plus1'] <- 'srpf_y_ss_iiss'
names(female)[names(female) == 'stq_y_ss_weekday_plus1'] <- 'stq_y_ss_weekday'
names(female)[names(female) == 'stq_y_ss_weekend_plus1'] <- 'stq_y_ss_weekend'

names(male)[names(male) == 'bis_y_ss_bas_rr_plus1'] <- 'bis_y_ss_bas_rr'
names(male)[names(male) == 'bis_y_ss_bas_drive_plus1'] <- 'bis_y_ss_bas_drive'
names(male)[names(male) == 'pgbi_p_ss_score_plus1'] <- 'pgbi_p_ss_score'
names(male)[names(male) == 'medhx_ss_4b_p_plus1'] <- 'medhx_ss_4b_p'
names(male)[names(male) == 'medhx_ss_5b_p_plus1'] <- 'medhx_ss_5b_p'
names(male)[names(male) == 'medhx_ss_6a_times_p_plus1'] <- 'medhx_ss_6a_times_p'
names(male)[names(male) == 'medhx_ss_6b_times_p_plus1'] <- 'medhx_ss_6b_times_p'
names(male)[names(male) == 'medhx_ss_6c_times_p_plus1'] <- 'medhx_ss_6c_times_p'
names(male)[names(male) == 'medhx_ss_6d_times_p_plus1'] <- 'medhx_ss_6d_times_p'
names(male)[names(male) == 'medhx_ss_6e_times_p_plus1'] <- 'medhx_ss_6e_times_p'
names(male)[names(male) == 'medhx_ss_6f_times_p_plus1'] <- 'medhx_ss_6f_times_p'
names(male)[names(male) == 'medhx_ss_6g_times_p_plus1'] <- 'medhx_ss_6g_times_p'
names(male)[names(male) == 'medhx_ss_6h_times_p_plus1'] <- 'medhx_ss_6h_times_p'
names(male)[names(male) == 'medhx_ss_6i_times_p_plus1'] <- 'medhx_ss_6i_times_p'
names(male)[names(male) == 'medhx_ss_6j_times_p_plus1'] <- 'medhx_ss_6j_times_p'
names(male)[names(male) == 'medhx_ss_6k_times_p_plus1'] <- 'medhx_ss_6k_times_p'
names(male)[names(male) == 'medhx_ss_6l_times_p_plus1'] <- 'medhx_ss_6l_times_p'
names(male)[names(male) == 'medhx_ss_6m_times_p_plus1'] <- 'medhx_ss_6m_times_p'
names(male)[names(male) == 'medhx_ss_6n_times_p_plus1'] <- 'medhx_ss_6n_times_p'
names(male)[names(male) == 'medhx_ss_6o_times_p_plus1'] <- 'medhx_ss_6o_times_p'
names(male)[names(male) == 'medhx_ss_6p_times_p_plus1'] <- 'medhx_ss_6p_times_p'
names(male)[names(male) == 'medhx_ss_6q_times_p_plus1'] <- 'medhx_ss_6q_times_p'
names(male)[names(male) == 'medhx_ss_6r_times_p_plus1'] <- 'medhx_ss_6r_times_p'
names(male)[names(male) == 'medhx_ss_6s_times_p_plus1'] <- 'medhx_ss_6s_times_p'
names(male)[names(male) == 'medhx_ss_9b_p_plus1'] <- 'medhx_ss_9b_p'
names(male)[names(male) == 'devhx_16_p_plus1'] <- 'devhx_16_p'
names(male)[names(male) == 'bis_y_ss_basm_rr_plus1'] <- 'bis_y_ss_basm_rr'
names(male)[names(male) == 'bis_y_ss_basm_drive_plus1'] <- 'bis_y_ss_basm_drive'
names(male)[names(male) == 'bis_y_ss_bas_fs_plus1'] <- 'bis_y_ss_bas_fs'
names(male)[names(male) == 'resiliency5a_y_plus1'] <- 'resiliency5a_y_p'
names(male)[names(male) == 'resiliency6a_y_plus1'] <- 'resiliency6a_y_p'
names(male)[names(male) == 'resiliency5b_y_plus1'] <- 'resiliency5b_y_p'
names(male)[names(male) == 'resiliency6b_y_plus1'] <- 'resiliency6b_y_p'
names(male)[names(male) == 'fes_p_ss_fc_pr_plus1'] <- 'fes_p_ss_fc_pr_p'
names(male)[names(male) == 'psb_p_ss_mean_plus1'] <- 'psb_p_ss_mean'
names(male)[names(male) == 'fes_y_ss_fc_pr_plus1'] <- 'fes_y_ss_fc_pr'
names(male)[names(male) == 'psb_y_ss_mean_plus1'] <- 'psb_y_ss_mean'
names(male)[names(male) == 'srpf_y_ss_iiss_plus1'] <- 'srpf_y_ss_iiss'
names(male)[names(male) == 'stq_y_ss_weekday_plus1'] <- 'stq_y_ss_weekday'
names(male)[names(male) == 'stq_y_ss_weekend_plus1'] <- 'stq_y_ss_weekend'
```

## PheWAS - All Subjects #
```{r}
bl <- colorRampPalette(c("navy","royalblue","lightskyblue"))(200)                       
re <- colorRampPalette(c("mistyrose", "red2","darkred"))(200)

# PheWAS - multiethnic cohort
datalist <- list(abcdData_baseline_C4_filtered)
names(datalist) <- c("abcdData_baseline_C4_filtered")

# Linear model
for (j in 1:length(datalist)) {
df.linear <- data.frame() 
  for (i in c(312:321, 72, 274:276, 303, 309, 2503:2505, 2530:2533, 2535)) {
    this_var = datalist[[j]][, i]
    my.model.0 <- lm(as.matrix(this_var) ~ c4b_expression + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                    data = datalist[[j]], na.action = na.omit)
    my.model.1 <- lm(as.matrix(this_var) ~ c4a_expression +  
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                    data = datalist[[j]], na.action = na.omit)
    my.model <- lm(as.matrix(this_var) ~ c4a_expression + c4b_expression + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                    data = datalist[[j]], na.action = na.omit)
    p1 <- anova(my.model.0, my.model, test = "F")
    p2 <- anova(my.model.1, my.model, test = "F")
    df.linear <- rbind(df.linear, data.frame(data = names(datalist)[j],
                               ID = colnames(datalist[[j]])[i], 
                               N = nobs(my.model),
                               beta_C4A = summary(my.model)$coefficients[2, 1],
                               beta_C4B = summary(my.model)$coefficients[3, 1],
                               stderr_C4A = summary(my.model)$coefficients[2, 2],
                               stderr_C4B = summary(my.model)$coefficients[3, 2],
                               P_C4A = p1[2, 6],
                               P_C4B = p2[2, 6]))
 
     }

# Gamma log-link
df.gamma <- data.frame() 
  for (i in c(10:16, 39, 41, 62:71, 73:81, 281:284, 286, 301, 302, 304, 305, 2557:2579, 2581:2585, 2587:2597)) { 
    this_var = datalist[[j]][, i]
    my.model.0 <- glm(as.matrix(this_var) ~ c4b_expression + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    my.model.1 <- glm(as.matrix(this_var) ~ c4a_expression + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    my.model <- glm(as.matrix(this_var) ~ c4a_expression + c4b_expression + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    p1 <- anova(my.model.0, my.model, test = "F")
    p2 <- anova(my.model.1, my.model, test = "F")
    df.gamma <- rbind(df.gamma, data.frame(data = names(datalist)[j],
                               ID = colnames(datalist[[j]])[i], 
                               N = nobs(my.model),
                               beta_C4A = summary(my.model)$coefficients[2, 1],
                               beta_C4B = summary(my.model)$coefficients[3, 1],
                               stderr_C4A = summary(my.model)$coefficients[2, 2],
                               stderr_C4B = summary(my.model)$coefficients[3, 2],
                               P_C4A = p1[2, 6],
                               P_C4B = p2[2, 6]))
 
  }

# Logistic
df.logistic <- data.frame() 
    for (i in c(82, 84, 90, 92, 98, 101, 108:112, 114:116, 118:123, 134:135, 137:138, 167, 170:171, 174:175, 201, 197, 193, 199, 237, 239, 251, 261:262, 250, 252, 263:264)) {
    this_var = datalist[[j]][, i]
    my.model.0 <- glm(as.matrix(this_var) ~ c4b_expression + 
                        interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                      data = datalist[[j]], na.action = na.omit, family = "binomial")  
    my.model.1 <- glm(as.matrix(this_var) ~ c4a_expression +  
                        interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                      data = datalist[[j]], na.action = na.omit, family = "binomial")  
    my.model <- glm(as.matrix(this_var) ~ c4a_expression + c4b_expression + 
                        interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                      data = datalist[[j]], na.action = na.omit, family = "binomial")  
    p1 <- anova(my.model.0, my.model, test = "Chisq")
    p2 <- anova(my.model.1, my.model, test = "Chisq")
    df.logistic <- rbind(df.logistic, data.frame(data = names(datalist)[j],
                               ID = colnames(datalist[[j]])[i], 
                               N = nobs(my.model),
                               beta_C4A = summary(my.model)$coefficients[2, 1],
                               beta_C4B = summary(my.model)$coefficients[3, 1],
                               stderr_C4A = summary(my.model)$coefficients[2, 2],
                               stderr_C4B = summary(my.model)$coefficients[3, 2],
                               P_C4A = p1[2, 5],
                               P_C4B = p2[2, 5]))
    }
    
# Psychosis Gamma log-link
df.psychosis.gamma <- data.frame() 
  for (i in c(2499:2500)) { 
    this_var = datalist[[j]][, i]
    my.model.0 <- glm(as.matrix(this_var) ~ c4b_expression + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    my.model.1 <- glm(as.matrix(this_var) ~ c4a_expression + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    my.model <- glm(as.matrix(this_var) ~ c4a_expression + c4b_expression + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    p1 <- anova(my.model.0, my.model, test = "F")
    p2 <- anova(my.model.1, my.model, test = "F")
    df.psychosis.gamma <- rbind(df.psychosis.gamma, data.frame(data = names(datalist)[j],
                               ID = colnames(datalist[[j]])[i], 
                               N = nobs(my.model),
                               beta_C4A = summary(my.model)$coefficients[2, 1],
                               beta_C4B = summary(my.model)$coefficients[3, 1],
                               stderr_C4A = summary(my.model)$coefficients[2, 2],
                               stderr_C4B = summary(my.model)$coefficients[3, 2],
                               P_C4A = p1[2, 6],
                               P_C4B = p2[2, 6]))
 
  }

# Psychosis Logistic
df.psychosis.logistic <- data.frame() 
    my.model.0 <- glm(Psychosis_wPQ_susp ~ c4b_expression  + 
                        interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                      data = datalist[[j]], na.action = na.omit, family = "binomial")  
    my.model.1 <- glm(Psychosis_wPQ_susp ~ c4a_expression + 
                        interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                      data = datalist[[j]], na.action = na.omit, family = "binomial")  
    my.model <- glm(Psychosis_wPQ_susp ~ c4a_expression + c4b_expression + 
                        interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                      data = datalist[[j]], na.action = na.omit, family = "binomial")  
    p1 <- anova(my.model.0, my.model, test = "Chisq")
    p2 <- anova(my.model.1, my.model, test = "Chisq")
    df.psychosis.logistic <- rbind(df.psychosis.logistic, data.frame(data = names(datalist)[j],
                               ID = "Psychosis_wPQ_susp", 
                               N = nobs(my.model),
                               beta_C4A = summary(my.model)$coefficients[2, 1],
                               beta_C4B = summary(my.model)$coefficients[3, 1],
                               stderr_C4A = summary(my.model)$coefficients[2, 2],
                               stderr_C4B = summary(my.model)$coefficients[3, 2],
                               P_C4A = p1[2, 5],
                               P_C4B = p2[2, 5]))

  
df.by.ancestry <- rbind(df.linear, df.gamma)
df.by.ancestry <- rbind(df.by.ancestry, df.logistic)
df.by.ancestry <- rbind(df.by.ancestry, df.psychosis.gamma)
df.by.ancestry <- rbind(df.by.ancestry, df.psychosis.logistic)
df.by.ancestry$FDR_C4A <- p.adjust(df.by.ancestry$P_C4A,'fdr')
df.by.ancestry$FDR_C4B <- p.adjust(df.by.ancestry$P_C4B,'fdr')
df.by.ancestry$Category <- ifelse(df.by.ancestry$ID %in% c("nihtbx_picvocab_fc", "nihtbx_flanker_fc", "nihtbx_list_fc", "nihtbx_cardsort_fc", "nihtbx_pattern_fc", "nihtbx_picture_fc", "nihtbx_reading_fc", "nihtbx_fluidcomp_fc", "nihtbx_cryst_fc", "nihtbx_totalcomp_fc", "lmt_scr_perc_correct", "pea_wiscv_tss"), "Cognition", ifelse(df.by.ancestry$ID %in% c("anthro_waist_cm", "anthroheightcalc", "anthroweightcalc"), "Anthropometrics", ifelse(df.by.ancestry$ID %in% c("bis_y_ss_bas_drive", "bis_y_ss_bas_fs", "bis_y_ss_bas_fs", "bis_y_ss_bas_rr", "bis_y_ss_basm_drive", "bis_y_ss_basm_rr", "bis_y_ss_bism_sum"), "BIS/BAS", ifelse(df.by.ancestry$ID %in% c("bpm_t_scr_attention_t", "bpm_t_scr_external_t", "bpm_t_scr_internal_t", "bpm_t_scr_totalprob_t"), "BRIEF",ifelse(df.by.ancestry$ID %in% c("cbcl_scr_07_ocd_t", "cbcl_scr_07_sct_t", "cbcl_scr_07_stress_t", "cbcl_scr_dsm5_adhd_t", "cbcl_scr_dsm5_anxdisord_t", "cbcl_scr_dsm5_conduct_t", "cbcl_scr_dsm5_depress_t", "cbcl_scr_dsm5_opposit_t", "cbcl_scr_dsm5_somaticpr_t", "cbcl_scr_syn_aggressive_t", "cbcl_scr_syn_anxdep_t", "cbcl_scr_syn_attention_t", "cbcl_scr_syn_external_t", "cbcl_scr_syn_internal_t", "cbcl_scr_syn_rulebreak_t", "cbcl_scr_syn_social_t", "cbcl_scr_syn_somatic_t", "cbcl_scr_syn_thought_t", "cbcl_scr_syn_totprob_t", "cbcl_scr_syn_withdep_t"), "CBCL", ifelse(df.by.ancestry$ID %in% c("devhx_16_p", "devhx_20_p", "devhx_21_p"), "Dev History", ifelse(df.by.ancestry$ID %in% c("fes_p_ss_fc_pr_p", "fes_y_ss_fc_pr", "latent_factor_ss_general_ses", "latent_factor_ss_perinatal", "latent_factor_ss_social", "srpf_y_ss_iiss", "stq_y_ss_weekday", "stq_y_ss_weekend"), "Environment", ifelse(df.by.ancestry$ID %in% c("hormone_scr_dhea_mean", "hormone_scr_ert_mean", "pds_p_ss_all_category_2", "hormone_scr_hse_mean"), "Hormones/Puberty", ifelse(df.by.ancestry$ID %in% c("ksads_1_842_p", "ksads_1_842_t", "ksads_1_847_p", "ksads_1_847_t", "ksads_10_869_p", "ksads_10_870_p", "ksads_10_914_p", "ksads_10_914_t", "ksads_11_917_p", "ksads_11_918_p", "ksads_11_919_p", "ksads_11_920_p", "ksads_14_853_p", "ksads_14_854_p", "ksads_14_855_p", "ksads_15_901_p", "ksads_15_902_p", "ksads_16_897_p", "ksads_16_899_p", "ksads_18_903_p", "ksads_2_833_p", "ksads_2_833_t", "ksads_2_837_p", "ksads_2_837_t", "ksads_2_839_p", "ksads_2_839_t", "ksads_23_945_p", "ksads_23_945_t", "ksads_23_946_t", "ksads_23_947_p", "ksads_23_947_t", "ksads_23_956_p", "ksads_23_956_t", "ksads_23_957_p", "ksads_23_957_t", "ksads_23_958_p", "ksads_23_958_t", "ksads_23_959_t", "ksads_4_829_p", "ksads_4_849_p", "ksads_7_862_p", "ksads_7_910_p", "ksads_8_863_p", "ksads_8_864_p", "ksads_8_912_p", "ksads_8_912_t", "ksads_9_867_p", "ksads_9_868_p"), "KSADS", ifelse(df.by.ancestry$ID %in% c("medhx_ss_4b_p", "medhx_ss_5b_p", "medhx_ss_6a_times_p", "medhx_ss_6b_times_p", "medhx_ss_6c_times_p", "medhx_ss_6d_times_p", "medhx_ss_6e_times_p", "medhx_ss_6f_times_p", "medhx_ss_6g_times_p", "medhx_ss_6h_times_p", "medhx_ss_6i_times_p", "medhx_ss_6j_times_p", "medhx_ss_6k_times_p", "medhx_ss_6l_times_p", "medhx_ss_6m_times_p", "medhx_ss_6n_times_p", "medhx_ss_6o_times_p", "medhx_ss_6p_times_p", "medhx_ss_6q_times_p", "medhx_ss_6s_times_p", "medhx_ss_9b_p"), "Medical History", ifelse(df.by.ancestry$ID %in% c("pgbi_p_ss_score", "upps_y_ss_lack_of_perseverance", "upps_y_ss_lack_of_planning", "upps_y_ss_negative_urgency", "upps_y_ss_positive_urgency", "upps_y_ss_sensation_seeking"), "Implusivity", ifelse(df.by.ancestry$ID %in% c("psb_p_ss_mean", "psb_y_ss_mean", "resiliency5a_y_p", "resiliency5b_y_p", "resiliency6a_y_p", "resiliency6b_y_p", "ssrs_p_ss_sum"), "Social Behavior", ifelse(df.by.ancestry$ID %in% c("sds_p_ss_da", "sds_p_ss_dims", "sds_p_ss_does", "sds_p_ss_sbd", "sds_p_ss_shy", "sds_p_ss_swtd", "sds_p_ss_total"), "Sleep", ifelse(df.by.ancestry$ID %in% c("pps_y_ss_number_plus1", "pps_y_ss_severity_score_plus1", "Psychosis_wPQ_susp"), "Psychosis", 0))))))))))))))

print(df.by.ancestry)

df.by.ancestry$Direction <- ifelse(df.by.ancestry$beta_C4A >= 0, "Positive", "Negative")
df.by.ancestry$ID.new <- df.by.ancestry$ID

df.by.ancestry[59, 14] = "UPPS: \n Lack of Planning"
df.by.ancestry[11, 14] = "CBCL: \n Total Problems \n T-Score"
df.by.ancestry[96, 14] = "Family Environment, \n Youth Report: \n Conflict"
df.by.ancestry[133, 14] = "KSADS: \n Bipolar & Related (past)"
df.by.ancestry[12, 14] = "Latent Factor: \n Economic, Social, \n Physiological Well-Being"
df.by.ancestry[61, 14] = "UPPS: \n Lack of Perseverance"
df.by.ancestry[140, 14] = "KSASD: \n Suicidal Ideation, \n Active, Non-Specific (present)"
df.by.ancestry[55, 14] = "BRIEF: \n Externalizing"
df.by.ancestry[14, 14] = "Latent Factor: \n Perinatal Health"
df.by.ancestry[13, 14] = "Latent Factor: \n Perceived \n Social Support"
df.by.ancestry[47, 14] = "CBCL: \n AHDH DSM5 \n T-Score"
df.by.ancestry[38, 14] = "CBCL: \n Thought Syndrome Scale \n T-Score"
df.by.ancestry[64, 14] = "PGBI: Mania"
df.by.ancestry[81, 14] = "Medical History: \n Animal Bite"
df.by.ancestry[43, 14] = "CBCL: \n Externalizing Syndrome Scale \n T-Score"
df.by.ancestry[21, 14] = "Development: \n Speech"
df.by.ancestry[94, 14] = "Family Environment, \n Parent Report: \n Conflict"
df.by.ancestry[139, 14] = "KSADS: \n Self Injurious Behavior \n w/o Suicidal Intent \n (present)"
df.by.ancestry[37, 14] = "CBCL: \n Social Syndrome Scale \n T-Score"
df.by.ancestry[52, 14] = "CBCL: \n Stress Scale \n T-Score"

plot <- ggplot(df.by.ancestry, aes(x=Category, y=-log10(P_C4A), shape=Direction)) + 
  geom_point(aes(col=Category, size=abs(beta_C4A), fill=Category)) + 
  scale_shape_manual(values=c(25,24)) +
  theme_classic() + 
  theme(axis.text.x = element_blank(), axis.ticks=element_blank()) + 
  labs(color="Category", size="Abs. Beta", x="Phenotypes", y="-log10(P)") + 
  geom_text_repel(data=. %>% 
                    mutate(label = ifelse(P_C4A < 0.05, as.character(ID.new), "")),
                  aes(label=label),
                  size=2.5,
                  box.padding = 1,
                  force = 1,
                  force_pull = 1,
                  min.segment.length = 0,
                  point.padding = 0,
                  direction = "both",
                  segment.linetype = 6,
                  segment.color = "gray",
                  segment.curvature = -1e-20,
                  arrow = arrow(length = unit(0.015, "npc")),
                  max.overlaps = Inf
  ) + 
  geom_hline(yintercept=-log10(0.05), color="red", size=1, alpha=0.3, linetype="dashed") +
  ggtitle("C4A PheWAS") 
  #theme(legend.position="none")
plot1 <- plot + ylim(0, 5)
plot1
ggsave(plot1, file = '../results/Figure2_Plot_PheWAS.Graph.pdf', device = cairo_pdf, width = 10, height=5, units = 'in')
}

# Association by ancestry - seperate ancestry groups
datalist <- list(afr, latinx, eur)
names(datalist) <- c("afr", "latinx", "eur")

# Linear model
for (j in 1:length(datalist)) {
df.linear <- data.frame() 
  for (i in c(312:321, 72, 274:276, 303, 309, 2503:2505, 2530:2533, 2535)) {
    this_var = datalist[[j]][, i]
    my.model.0 <- lm(as.matrix(this_var) ~ c4b_expression + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                    data = datalist[[j]], na.action = na.omit)
    my.model.1 <- lm(as.matrix(this_var) ~ c4a_expression +  
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                    data = datalist[[j]], na.action = na.omit)
    my.model <- lm(as.matrix(this_var) ~ c4a_expression + c4b_expression + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                    data = datalist[[j]], na.action = na.omit)
    p1 <- anova(my.model.0, my.model, test = "F")
    p2 <- anova(my.model.1, my.model, test = "F")
    df.linear <- rbind(df.linear, data.frame(data = names(datalist)[j],
                               ID = colnames(datalist[[j]])[i], 
                               N = nobs(my.model),
                               beta_C4A = summary(my.model)$coefficients[2, 1],
                               beta_C4B = summary(my.model)$coefficients[3, 1],
                               stderr_C4A = summary(my.model)$coefficients[2, 2],
                               stderr_C4B = summary(my.model)$coefficients[3, 2],
                               P_C4A = p1[2, 6],
                               P_C4B = p2[2, 6]))
 
     }

# Gamma log-link
df.gamma <- data.frame() 
  for (i in c(10:16, 39, 41, 62:71, 73:81, 281:284, 286, 301, 302, 304, 305, 2557:2579, 2581:2585, 2587:2597)) { 
    this_var = datalist[[j]][, i]
    my.model.0 <- glm(as.matrix(this_var) ~ c4b_expression + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    my.model.1 <- glm(as.matrix(this_var) ~ c4a_expression + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    my.model <- glm(as.matrix(this_var) ~ c4a_expression + c4b_expression + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    p1 <- anova(my.model.0, my.model, test = "F")
    p2 <- anova(my.model.1, my.model, test = "F")
    df.gamma <- rbind(df.gamma, data.frame(data = names(datalist)[j],
                               ID = colnames(datalist[[j]])[i], 
                               N = nobs(my.model),
                               beta_C4A = summary(my.model)$coefficients[2, 1],
                               beta_C4B = summary(my.model)$coefficients[3, 1],
                               stderr_C4A = summary(my.model)$coefficients[2, 2],
                               stderr_C4B = summary(my.model)$coefficients[3, 2],
                               P_C4A = p1[2, 6],
                               P_C4B = p2[2, 6]))
 
  }

# Logistic
df.logistic <- data.frame() 
    for (i in c(82, 84, 90, 92, 98, 101, 108:112, 114:116, 118:123, 134:135, 137:138, 167, 170:171, 174:175, 201, 197, 193, 199, 237, 239, 251, 261:262, 250, 252, 263:264)) {
    this_var = datalist[[j]][, i]
    my.model.0 <- glm(as.matrix(this_var) ~ c4b_expression + 
                        interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                      data = datalist[[j]], na.action = na.omit, family = "binomial")  
    my.model.1 <- glm(as.matrix(this_var) ~ c4a_expression +  
                        interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                      data = datalist[[j]], na.action = na.omit, family = "binomial")  
    my.model <- glm(as.matrix(this_var) ~ c4a_expression + c4b_expression + 
                        interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                      data = datalist[[j]], na.action = na.omit, family = "binomial")  
    p1 <- anova(my.model.0, my.model, test = "Chisq")
    p2 <- anova(my.model.1, my.model, test = "Chisq")
    df.logistic <- rbind(df.logistic, data.frame(data = names(datalist)[j],
                               ID = colnames(datalist[[j]])[i], 
                               N = nobs(my.model),
                               beta_C4A = summary(my.model)$coefficients[2, 1],
                               beta_C4B = summary(my.model)$coefficients[3, 1],
                               stderr_C4A = summary(my.model)$coefficients[2, 2],
                               stderr_C4B = summary(my.model)$coefficients[3, 2],
                               P_C4A = p1[2, 5],
                               P_C4B = p2[2, 5]))
    }
    
# Psychosis Gamma log-link
df.psychosis.gamma <- data.frame() 
  for (i in c(2499:2500)) { 
    this_var = datalist[[j]][, i]
    my.model.0 <- glm(as.matrix(this_var) ~ c4b_expression + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    my.model.1 <- glm(as.matrix(this_var) ~ c4a_expression + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    my.model <- glm(as.matrix(this_var) ~ c4a_expression + c4b_expression + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    p1 <- anova(my.model.0, my.model, test = "F")
    p2 <- anova(my.model.1, my.model, test = "F")
    df.psychosis.gamma <- rbind(df.psychosis.gamma, data.frame(data = names(datalist)[j],
                               ID = colnames(datalist[[j]])[i], 
                               N = nobs(my.model),
                               beta_C4A = summary(my.model)$coefficients[2, 1],
                               beta_C4B = summary(my.model)$coefficients[3, 1],
                               stderr_C4A = summary(my.model)$coefficients[2, 2],
                               stderr_C4B = summary(my.model)$coefficients[3, 2],
                               P_C4A = p1[2, 6],
                               P_C4B = p2[2, 6]))
 
  }

# Psychosis Logistic
df.psychosis.logistic <- data.frame() 
    my.model.0 <- glm(Psychosis_wPQ_susp ~ c4b_expression  + 
                        interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                      data = datalist[[j]], na.action = na.omit, family = "binomial")  
    my.model.1 <- glm(Psychosis_wPQ_susp ~ c4a_expression + 
                        interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                      data = datalist[[j]], na.action = na.omit, family = "binomial")  
    my.model <- glm(Psychosis_wPQ_susp ~ c4a_expression + c4b_expression + 
                        interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + site_id_l, 
                      data = datalist[[j]], na.action = na.omit, family = "binomial")  
    p1 <- anova(my.model.0, my.model, test = "Chisq")
    p2 <- anova(my.model.1, my.model, test = "Chisq")
    df.psychosis.logistic <- rbind(df.psychosis.logistic, data.frame(data = names(datalist)[j],
                               ID = "Psychosis_wPQ_susp", 
                               N = nobs(my.model),
                               beta_C4A = summary(my.model)$coefficients[2, 1],
                               beta_C4B = summary(my.model)$coefficients[3, 1],
                               stderr_C4A = summary(my.model)$coefficients[2, 2],
                               stderr_C4B = summary(my.model)$coefficients[3, 2],
                               P_C4A = p1[2, 5],
                               P_C4B = p2[2, 5]))

  
df.by.ancestry <- rbind(df.linear, df.gamma)
df.by.ancestry <- rbind(df.by.ancestry, df.logistic)
df.by.ancestry <- rbind(df.by.ancestry, df.psychosis.gamma)
df.by.ancestry <- rbind(df.by.ancestry, df.psychosis.logistic)
df.by.ancestry$FDR_C4A <- p.adjust(df.by.ancestry$P_C4A,'fdr')
df.by.ancestry$FDR_C4B <- p.adjust(df.by.ancestry$P_C4B,'fdr')
df.by.ancestry$Category <- ifelse(df.by.ancestry$ID %in% c("nihtbx_picvocab_fc", "nihtbx_flanker_fc", "nihtbx_list_fc", "nihtbx_cardsort_fc", "nihtbx_pattern_fc", "nihtbx_picture_fc", "nihtbx_reading_fc", "nihtbx_fluidcomp_fc", "nihtbx_cryst_fc", "nihtbx_totalcomp_fc", "lmt_scr_perc_correct", "pea_wiscv_tss"), "Cognition", ifelse(df.by.ancestry$ID %in% c("anthro_waist_cm", "anthroheightcalc", "anthroweightcalc"), "Anthropometrics", ifelse(df.by.ancestry$ID %in% c("bis_y_ss_bas_drive", "bis_y_ss_bas_fs", "bis_y_ss_bas_fs", "bis_y_ss_bas_rr", "bis_y_ss_basm_drive", "bis_y_ss_basm_rr", "bis_y_ss_bism_sum"), "BIS/BAS", ifelse(df.by.ancestry$ID %in% c("bpm_t_scr_attention_t", "bpm_t_scr_external_t", "bpm_t_scr_internal_t", "bpm_t_scr_totalprob_t"), "BRIEF",ifelse(df.by.ancestry$ID %in% c("cbcl_scr_07_ocd_t", "cbcl_scr_07_sct_t", "cbcl_scr_07_stress_t", "cbcl_scr_dsm5_adhd_t", "cbcl_scr_dsm5_anxdisord_t", "cbcl_scr_dsm5_conduct_t", "cbcl_scr_dsm5_depress_t", "cbcl_scr_dsm5_opposit_t", "cbcl_scr_dsm5_somaticpr_t", "cbcl_scr_syn_aggressive_t", "cbcl_scr_syn_anxdep_t", "cbcl_scr_syn_attention_t", "cbcl_scr_syn_external_t", "cbcl_scr_syn_internal_t", "cbcl_scr_syn_rulebreak_t", "cbcl_scr_syn_social_t", "cbcl_scr_syn_somatic_t", "cbcl_scr_syn_thought_t", "cbcl_scr_syn_totprob_t", "cbcl_scr_syn_withdep_t"), "CBCL", ifelse(df.by.ancestry$ID %in% c("devhx_16_p", "devhx_20_p", "devhx_21_p"), "Dev History", ifelse(df.by.ancestry$ID %in% c("fes_p_ss_fc_pr_p", "fes_y_ss_fc_pr", "latent_factor_ss_general_ses", "latent_factor_ss_perinatal", "latent_factor_ss_social", "srpf_y_ss_iiss", "stq_y_ss_weekday", "stq_y_ss_weekend"), "Environment", ifelse(df.by.ancestry$ID %in% c("hormone_scr_dhea_mean", "hormone_scr_ert_mean", "pds_p_ss_all_category_2", "hormone_scr_hse_mean"), "Hormones/Puberty", ifelse(df.by.ancestry$ID %in% c("ksads_1_842_p", "ksads_1_842_t", "ksads_1_847_p", "ksads_1_847_t", "ksads_10_869_p", "ksads_10_870_p", "ksads_10_914_p", "ksads_10_914_t", "ksads_11_917_p", "ksads_11_918_p", "ksads_11_919_p", "ksads_11_920_p", "ksads_14_853_p", "ksads_14_854_p", "ksads_14_855_p", "ksads_15_901_p", "ksads_15_902_p", "ksads_16_897_p", "ksads_16_899_p", "ksads_18_903_p", "ksads_2_833_p", "ksads_2_833_t", "ksads_2_837_p", "ksads_2_837_t", "ksads_2_839_p", "ksads_2_839_t", "ksads_23_945_p", "ksads_23_945_t", "ksads_23_946_t", "ksads_23_947_p", "ksads_23_947_t", "ksads_23_956_p", "ksads_23_956_t", "ksads_23_957_p", "ksads_23_957_t", "ksads_23_958_p", "ksads_23_958_t", "ksads_23_959_t", "ksads_4_829_p", "ksads_4_849_p", "ksads_7_862_p", "ksads_7_910_p", "ksads_8_863_p", "ksads_8_864_p", "ksads_8_912_p", "ksads_8_912_t", "ksads_9_867_p", "ksads_9_868_p"), "KSADS", ifelse(df.by.ancestry$ID %in% c("medhx_ss_4b_p", "medhx_ss_5b_p", "medhx_ss_6a_times_p", "medhx_ss_6b_times_p", "medhx_ss_6c_times_p", "medhx_ss_6d_times_p", "medhx_ss_6e_times_p", "medhx_ss_6f_times_p", "medhx_ss_6g_times_p", "medhx_ss_6h_times_p", "medhx_ss_6i_times_p", "medhx_ss_6j_times_p", "medhx_ss_6k_times_p", "medhx_ss_6l_times_p", "medhx_ss_6m_times_p", "medhx_ss_6n_times_p", "medhx_ss_6o_times_p", "medhx_ss_6p_times_p", "medhx_ss_6q_times_p", "medhx_ss_6s_times_p", "medhx_ss_9b_p"), "Medical History", ifelse(df.by.ancestry$ID %in% c("pgbi_p_ss_score", "upps_y_ss_lack_of_perseverance", "upps_y_ss_lack_of_planning", "upps_y_ss_negative_urgency", "upps_y_ss_positive_urgency", "upps_y_ss_sensation_seeking"), "Implusivity", ifelse(df.by.ancestry$ID %in% c("psb_p_ss_mean", "psb_y_ss_mean", "resiliency5a_y_p", "resiliency5b_y_p", "resiliency6a_y_p", "resiliency6b_y_p", "ssrs_p_ss_sum"), "Social Behavior", ifelse(df.by.ancestry$ID %in% c("sds_p_ss_da", "sds_p_ss_dims", "sds_p_ss_does", "sds_p_ss_sbd", "sds_p_ss_shy", "sds_p_ss_swtd", "sds_p_ss_total"), "Sleep", ifelse(df.by.ancestry$ID %in% c("pps_y_ss_number_plus1", "pps_y_ss_severity_score_plus1", "Psychosis_wPQ_susp"), "Psychosis", 0))))))))))))))

print(df.by.ancestry)

df.by.ancestry$Direction <- ifelse(df.by.ancestry$beta_C4A >= 0, "Positive", "Negative")

plot <- ggplot(df.by.ancestry, aes(x=Category, y=-log10(P_C4A), shape=Direction)) + 
  geom_point(aes(col=Category, size=abs(beta_C4A), fill=Category)) + 
  scale_shape_manual(values=c(25,24)) +
  theme_classic() + 
  theme(axis.text.x = element_blank(), axis.ticks=element_blank()) + 
  labs(color="Category", size="Abs. Beta", x="Phenotypes", y="-log10(P)") + 
  geom_text_repel(data=. %>% 
                    mutate(label = ifelse(P_C4A < 0.05, as.character(ID), "")),
                  aes(label=label),
                  size=3,
                  box.padding = 1,
                  force = 1,
                  force_pull = 1,
                  min.segment.length = 0,
                  point.padding = 0,
                  direction = "both",
                  segment.linetype = 6,
                  segment.color = "gray",
                  segment.curvature = -1e-20,
                  arrow = arrow(length = unit(0.015, "npc")),
                  max.overlaps = Inf
  ) + 
  geom_hline(yintercept=-log10(0.05), color="red", size=1, alpha=0.3, linetype="dashed") +
  ggtitle("C4A PheWAS")
print(plot + ylim(0, 5))
}
```

## PheWAS - sex interaction #
```{r}
# PheWAS - multiethnic cohort
datalist <- list(abcdData_baseline_C4_filtered)
names(datalist) <- c("abcdData_baseline_C4_filtered")

# Linear model
for (j in 1:length(datalist)) {
df.linear <- data.frame() 
  for (i in c(312:321, 72, 274:276, 303, 309, 2503:2505, 2530:2533, 2535)) {
    this_var = datalist[[j]][, i]
    my.model.0 <- lm(as.matrix(this_var) ~ c4b_expression * sex + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                    data = datalist[[j]], na.action = na.omit)
    my.model.1 <- lm(as.matrix(this_var) ~ c4a_expression * sex + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                    data = datalist[[j]], na.action = na.omit)
    my.model <- lm(as.matrix(this_var) ~ c4a_expression * sex + c4b_expression * sex + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                    data = datalist[[j]], na.action = na.omit)
    p1 <- anova(my.model.0, my.model, test = "F")
    p2 <- anova(my.model.1, my.model, test = "F")
    df.linear <- rbind(df.linear, data.frame(data = names(datalist)[j],
                               ID = colnames(datalist[[j]])[i], 
                               N = nobs(my.model),
                               beta_C4A = summary(my.model)$coefficients[32, 1],
                               beta_C4B = summary(my.model)$coefficients[33, 1],
                               stderr_C4A = summary(my.model)$coefficients[32, 2],
                               stderr_C4B = summary(my.model)$coefficients[33, 2],
                               P_C4A = p1[2, 6],
                               P_C4B = p2[2, 6]))
  }


# Gamma log-link
df.gamma1 <- data.frame() 
  for (i in c(10:16, 39, 41, 62:71, 73:81, 282:283, 286, 301, 302, 304, 305, 2557:2579, 2581:2585, 2587:2597)) { 
    #for (i in c(284)) {
    this_var = datalist[[j]][, i]
    my.model.0 <- glm(as.matrix(this_var) ~ c4b_expression * sex + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    my.model.1 <- glm(as.matrix(this_var) ~ c4a_expression * sex + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    my.model <- glm(as.matrix(this_var) ~ c4a_expression * sex + c4b_expression * sex + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    p1 <- anova(my.model.0, my.model, test = "F")
    p2 <- anova(my.model.1, my.model, test = "F")
    df.gamma1 <- rbind(df.gamma1, data.frame(data = names(datalist)[j],
                               ID = colnames(datalist[[j]])[i], 
                               N = nobs(my.model),
                               beta_C4A = summary(my.model)$coefficients[32, 1],
                               beta_C4B = summary(my.model)$coefficients[33, 1],
                               stderr_C4A = summary(my.model)$coefficients[32, 2],
                               stderr_C4B = summary(my.model)$coefficients[33, 2],
                               P_C4A = p1[2, 6],
                               P_C4B = p2[2, 6]))
  }

df.gamma2 <- data.frame() 
  for (i in c(281, 284)) { 
    this_var = datalist[[j]][, i]
    my.model.0 <- glm(as.matrix(this_var) ~ c4b_expression * sex + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    my.model.1 <- glm(as.matrix(this_var) ~ c4a_expression * sex + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    my.model <- glm(as.matrix(this_var) ~ c4a_expression * sex + c4b_expression * sex + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    p1 <- anova(my.model.0, my.model, test = "F")
    p2 <- anova(my.model.1, my.model, test = "F")
    df.gamma2 <- rbind(df.gamma2, data.frame(data = names(datalist)[j],
                               ID = colnames(datalist[[j]])[i], 
                               N = nobs(my.model),
                               beta_C4A = summary(my.model)$coefficients[31, 1],
                               beta_C4B = summary(my.model)$coefficients[32, 1],
                               stderr_C4A = summary(my.model)$coefficients[31, 2],
                               stderr_C4B = summary(my.model)$coefficients[32, 2],
                               P_C4A = p1[2, 6],
                               P_C4B = p2[2, 6]))
  }

# Logistic
df.logistic <- data.frame() 
    for (i in c(82, 84, 90, 92, 98, 101, 108:112, 114:116, 118:123, 134:135, 137:138, 167, 170:171, 174:175, 201, 197, 193, 199, 237, 239, 251, 261:262, 250, 252, 263:264)) {
    this_var = datalist[[j]][, i]
    my.model.0 <- glm(as.matrix(this_var) ~ c4b_expression * sex + 
                        interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                      data = datalist[[j]], na.action = na.omit, family = "binomial")  
    my.model.1 <- glm(as.matrix(this_var) ~ c4a_expression * sex + 
                        interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                      data = datalist[[j]], na.action = na.omit, family = "binomial")  
    my.model <- glm(as.matrix(this_var) ~ c4a_expression * sex + c4b_expression * sex + 
                        interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                      data = datalist[[j]], na.action = na.omit, family = "binomial")  
    p1 <- anova(my.model.0, my.model, test = "Chisq")
    p2 <- anova(my.model.1, my.model, test = "Chisq")
    df.logistic <- rbind(df.logistic, data.frame(data = names(datalist)[j],
                               ID = colnames(datalist[[j]])[i], 
                               N = nobs(my.model),
                               beta_C4A = summary(my.model)$coefficients[32, 1],
                               beta_C4B = summary(my.model)$coefficients[33, 1],
                               stderr_C4A = summary(my.model)$coefficients[32, 2],
                               stderr_C4B = summary(my.model)$coefficients[33, 2],
                               P_C4A = p1[2, 5],
                               P_C4B = p2[2, 5]))
    }

    
# Psychosis Gamma log-link
df.psychosis.gamma <- data.frame() 
  for (i in c(2499:2500)) { 
    this_var = datalist[[j]][, i]
    my.model.0 <- glm(as.matrix(this_var) ~ c4b_expression * sex + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    my.model.1 <- glm(as.matrix(this_var) ~ c4a_expression * sex + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    my.model <- glm(as.matrix(this_var) ~ c4a_expression * sex + c4b_expression * sex + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    p1 <- anova(my.model.0, my.model, test = "F")
    p2 <- anova(my.model.1, my.model, test = "F")
    df.psychosis.gamma <- rbind(df.psychosis.gamma, data.frame(data = names(datalist)[j],
                               ID = colnames(datalist[[j]])[i], 
                               N = nobs(my.model),
                               beta_C4A = summary(my.model)$coefficients[32, 1],
                               beta_C4B = summary(my.model)$coefficients[33, 1],
                               stderr_C4A = summary(my.model)$coefficients[32, 2],
                               stderr_C4B = summary(my.model)$coefficients[33, 2],
                               P_C4A = p1[2, 6],
                               P_C4B = p2[2, 6]))
 
  }

# Psychosis Logistic
df.psychosis.logistic <- data.frame() 
    my.model.0 <- glm(Psychosis_wPQ_susp ~ c4b_expression* sex  + 
                        interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                      data = datalist[[j]], na.action = na.omit, family = "binomial")  
    my.model.1 <- glm(Psychosis_wPQ_susp ~ c4a_expression * sex + 
                        interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                      data = datalist[[j]], na.action = na.omit, family = "binomial")  
    my.model <- glm(Psychosis_wPQ_susp ~ c4a_expression * sex  + c4b_expression * sex  + 
                        interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                      data = datalist[[j]], na.action = na.omit, family = "binomial")  
    p1 <- anova(my.model.0, my.model, test = "Chisq")
    p2 <- anova(my.model.1, my.model, test = "Chisq")
    df.psychosis.logistic <- rbind(df.psychosis.logistic, data.frame(data = names(datalist)[j],
                               ID = "Psychosis_wPQ_susp", 
                               N = nobs(my.model),
                               beta_C4A = summary(my.model)$coefficients[32, 1],
                               beta_C4B = summary(my.model)$coefficients[33, 1],
                               stderr_C4A = summary(my.model)$coefficients[32, 2],
                               stderr_C4B = summary(my.model)$coefficients[33, 2],
                               P_C4A = p1[2, 5],
                               P_C4B = p2[2, 5]))
}

df.sex.interaction <- rbind(df.linear, df.gamma1)
df.sex.interaction <- rbind(df.sex.interaction, df.gamma2)
df.sex.interaction <- rbind(df.sex.interaction, df.logistic)
df.sex.interaction <- rbind(df.sex.interaction, df.psychosis.gamma)
df.sex.interaction <- rbind(df.sex.interaction, df.psychosis.logistic)
df.sex.interaction$FDR_C4A <- p.adjust(df.sex.interaction$P_C4A,'fdr')
df.sex.interaction$FDR_C4B <- p.adjust(df.sex.interaction$P_C4B,'fdr')
df.sex.interaction$Category <- ifelse(df.sex.interaction$ID %in% c("nihtbx_picvocab_fc", "nihtbx_flanker_fc", "nihtbx_list_fc", "nihtbx_cardsort_fc", "nihtbx_pattern_fc", "nihtbx_picture_fc", "nihtbx_reading_fc", "nihtbx_fluidcomp_fc", "nihtbx_cryst_fc", "nihtbx_totalcomp_fc", "lmt_scr_perc_correct", "pea_wiscv_tss"), "Cognition", ifelse(df.sex.interaction$ID %in% c("anthro_waist_cm", "anthroheightcalc", "anthroweightcalc"), "Anthropometrics", ifelse(df.sex.interaction$ID %in% c("bis_y_ss_bas_drive", "bis_y_ss_bas_fs", "bis_y_ss_bas_fs", "bis_y_ss_bas_rr", "bis_y_ss_basm_drive", "bis_y_ss_basm_rr", "bis_y_ss_bism_sum"), "BIS/BAS", ifelse(df.sex.interaction$ID %in% c("bpm_t_scr_attention_t", "bpm_t_scr_external_t", "bpm_t_scr_internal_t", "bpm_t_scr_totalprob_t"), "BRIEF",ifelse(df.sex.interaction$ID %in% c("cbcl_scr_07_ocd_t", "cbcl_scr_07_sct_t", "cbcl_scr_07_stress_t", "cbcl_scr_dsm5_adhd_t", "cbcl_scr_dsm5_anxdisord_t", "cbcl_scr_dsm5_conduct_t", "cbcl_scr_dsm5_depress_t", "cbcl_scr_dsm5_opposit_t", "cbcl_scr_dsm5_somaticpr_t", "cbcl_scr_syn_aggressive_t", "cbcl_scr_syn_anxdep_t", "cbcl_scr_syn_attention_t", "cbcl_scr_syn_external_t", "cbcl_scr_syn_internal_t", "cbcl_scr_syn_rulebreak_t", "cbcl_scr_syn_social_t", "cbcl_scr_syn_somatic_t", "cbcl_scr_syn_thought_t", "cbcl_scr_syn_totprob_t", "cbcl_scr_syn_withdep_t"), "CBCL", ifelse(df.sex.interaction$ID %in% c("devhx_16_p", "devhx_20_p", "devhx_21_p"), "Dev History", ifelse(df.sex.interaction$ID %in% c("fes_p_ss_fc_pr_p", "fes_y_ss_fc_pr", "latent_factor_ss_general_ses", "latent_factor_ss_perinatal", "latent_factor_ss_social", "srpf_y_ss_iiss", "stq_y_ss_weekday", "stq_y_ss_weekend"), "Environment", ifelse(df.sex.interaction$ID %in% c("hormone_scr_dhea_mean", "hormone_scr_ert_mean", "pds_p_ss_all_category_2", "hormone_scr_hse_mean"), "Hormones/Puberty", ifelse(df.sex.interaction$ID %in% c("ksads_1_842_p", "ksads_1_842_t", "ksads_1_847_p", "ksads_1_847_t", "ksads_10_869_p", "ksads_10_870_p", "ksads_10_914_p", "ksads_10_914_t", "ksads_11_917_p", "ksads_11_918_p", "ksads_11_919_p", "ksads_11_920_p", "ksads_14_853_p", "ksads_14_854_p", "ksads_14_855_p", "ksads_15_901_p", "ksads_15_902_p", "ksads_16_897_p", "ksads_16_899_p", "ksads_18_903_p", "ksads_2_833_p", "ksads_2_833_t", "ksads_2_837_p", "ksads_2_837_t", "ksads_2_839_p", "ksads_2_839_t", "ksads_23_945_p", "ksads_23_945_t", "ksads_23_946_t", "ksads_23_947_p", "ksads_23_947_t", "ksads_23_956_p", "ksads_23_956_t", "ksads_23_957_p", "ksads_23_957_t", "ksads_23_958_p", "ksads_23_958_t", "ksads_23_959_t", "ksads_4_829_p", "ksads_4_849_p", "ksads_7_862_p", "ksads_7_910_p", "ksads_8_863_p", "ksads_8_864_p", "ksads_8_912_p", "ksads_8_912_t", "ksads_9_867_p", "ksads_9_868_p"), "KSADS", ifelse(df.sex.interaction$ID %in% c("medhx_ss_4b_p", "medhx_ss_5b_p", "medhx_ss_6a_times_p", "medhx_ss_6b_times_p", "medhx_ss_6c_times_p", "medhx_ss_6d_times_p", "medhx_ss_6e_times_p", "medhx_ss_6f_times_p", "medhx_ss_6g_times_p", "medhx_ss_6h_times_p", "medhx_ss_6i_times_p", "medhx_ss_6j_times_p", "medhx_ss_6k_times_p", "medhx_ss_6l_times_p", "medhx_ss_6m_times_p", "medhx_ss_6n_times_p", "medhx_ss_6o_times_p", "medhx_ss_6p_times_p", "medhx_ss_6q_times_p", "medhx_ss_6s_times_p", "medhx_ss_9b_p"), "Medical History", ifelse(df.sex.interaction$ID %in% c("pgbi_p_ss_score", "upps_y_ss_lack_of_perseverance", "upps_y_ss_lack_of_planning", "upps_y_ss_negative_urgency", "upps_y_ss_positive_urgency", "upps_y_ss_sensation_seeking"), "Implusivity", ifelse(df.sex.interaction$ID %in% c("psb_p_ss_mean", "psb_y_ss_mean", "resiliency5a_y_p", "resiliency5b_y_p", "resiliency6a_y_p", "resiliency6b_y_p", "ssrs_p_ss_sum"), "Social Behavior", ifelse(df.sex.interaction$ID %in% c("sds_p_ss_da", "sds_p_ss_dims", "sds_p_ss_does", "sds_p_ss_sbd", "sds_p_ss_shy", "sds_p_ss_swtd", "sds_p_ss_total"), "Sleep", ifelse(df.sex.interaction$ID %in% c("pps_y_ss_number_plus1", "pps_y_ss_severity_score_plus1", "Psychosis_wPQ_susp"), "Psychosis", 0))))))))))))))

print(df.sex.interaction)

df.sex.interaction$Direction <- ifelse(df.sex.interaction$beta_C4A >= 0, "Positive", "Negative")

plot <- ggplot(df.sex.interaction, aes(x=Category, y=-log10(P_C4A), shape=Direction)) + 
  geom_point(aes(col=Category, size=abs(beta_C4A), fill=Category)) + 
  scale_shape_manual(values=c(25,24)) +
  theme_classic() + 
  theme(axis.text.x = element_blank(), axis.ticks=element_blank()) + 
  labs(color="Category", size="Abs. Beta", x="Phenotypes", y="-log10(P)") + 
  geom_text_repel(data=. %>% 
                    mutate(label = ifelse(P_C4A < 0.05, as.character(ID), "")),
                  aes(label=label),
                  size=3,
                  box.padding = 1,
                  force = 1,
                  force_pull = 1,
                  min.segment.length = 0,
                  point.padding = 0,
                  direction = "both",
                  segment.linetype = 6,
                  segment.color = "gray",
                  segment.curvature = -1e-20,
                  arrow = arrow(length = unit(0.015, "npc")),
                  max.overlaps = Inf
  ) + 
  geom_hline(yintercept=-log10(0.05), color="red", size=1, alpha=0.3, linetype="dashed") +
  ggtitle("C4A PheWAS")
print(plot + ylim(0, 5))
```

## PheWAS - by sex #
```{r}
# Association by sex
datalist <- list(female, male)
names(datalist) <- c("female", "male")

# Linear model
for (j in 1:length(datalist)) {
df.linear <- data.frame() 
  for (i in c(312:321, 72, 274:276, 303, 309, 2503:2505, 2530:2533, 2535)) {
    this_var = datalist[[j]][, i]
    my.model.0 <- lm(as.matrix(this_var) ~ c4b_expression + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                    data = datalist[[j]], na.action = na.omit)
    my.model.1 <- lm(as.matrix(this_var) ~ c4a_expression + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                    data = datalist[[j]], na.action = na.omit)
    my.model <- lm(as.matrix(this_var) ~ c4a_expression + c4b_expression + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                    data = datalist[[j]], na.action = na.omit)
    p1 <- anova(my.model.0, my.model, test = "F")
    p2 <- anova(my.model.1, my.model, test = "F")
    df.linear <- rbind(df.linear, data.frame(data = names(datalist)[j],
                               ID = colnames(datalist[[j]])[i], 
                               N = nobs(my.model),
                               beta_C4A = summary(my.model)$coefficients[2, 1],
                               beta_C4B = summary(my.model)$coefficients[3, 1],
                               stderr_C4A = summary(my.model)$coefficients[2, 2],
                               stderr_C4B = summary(my.model)$coefficients[3, 2],
                               P_C4A = p1[2, 6],
                               P_C4B = p2[2, 6]))
  }


# Gamma log-link
df.gamma1 <- data.frame() 
  for (i in c(10:16, 39, 41, 62:71, 73:81, 282:283, 286, 301, 302, 304, 305, 2557:2579, 2581:2585, 2587:2597)) { 
    #for (i in c(284)) {
    this_var = datalist[[j]][, i]
    my.model.0 <- glm(as.matrix(this_var) ~ c4b_expression + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    my.model.1 <- glm(as.matrix(this_var) ~ c4a_expression + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    my.model <- glm(as.matrix(this_var) ~ c4a_expression + c4b_expression + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    p1 <- anova(my.model.0, my.model, test = "F")
    p2 <- anova(my.model.1, my.model, test = "F")
    df.gamma1 <- rbind(df.gamma1, data.frame(data = names(datalist)[j],
                               ID = colnames(datalist[[j]])[i], 
                               N = nobs(my.model),
                               beta_C4A = summary(my.model)$coefficients[2, 1],
                               beta_C4B = summary(my.model)$coefficients[3, 1],
                               stderr_C4A = summary(my.model)$coefficients[2, 2],
                               stderr_C4B = summary(my.model)$coefficients[3, 2],
                               P_C4A = p1[2, 6],
                               P_C4B = p2[2, 6]))
  }

df.gamma2 <- data.frame() 
  for (i in c(281, 284)) { 
    this_var = datalist[[j]][, i]
    my.model.0 <- glm(as.matrix(this_var) ~ c4b_expression + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    my.model.1 <- glm(as.matrix(this_var) ~ c4a_expression + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    my.model <- glm(as.matrix(this_var) ~ c4a_expression + c4b_expression + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    p1 <- anova(my.model.0, my.model, test = "F")
    p2 <- anova(my.model.1, my.model, test = "F")
    df.gamma2 <- rbind(df.gamma2, data.frame(data = names(datalist)[j],
                               ID = colnames(datalist[[j]])[i], 
                               N = nobs(my.model),
                               beta_C4A = summary(my.model)$coefficients[2, 1],
                               beta_C4B = summary(my.model)$coefficients[3, 1],
                               stderr_C4A = summary(my.model)$coefficients[2, 2],
                               stderr_C4B = summary(my.model)$coefficients[3, 2],
                               P_C4A = p1[2, 6],
                               P_C4B = p2[2, 6]))
  }

# Logistic
df.logistic <- data.frame() 
    for (i in c(82, 84, 90, 92, 98, 101, 108:112, 114:116, 118:123, 134:135, 137:138, 167, 170:171, 174:175, 201, 197, 193, 199, 237, 239, 251, 261:262, 250, 252, 263:264)) {
    this_var = datalist[[j]][, i]
    my.model.0 <- glm(as.matrix(this_var) ~ c4b_expression + 
                        interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                      data = datalist[[j]], na.action = na.omit, family = "binomial")  
    my.model.1 <- glm(as.matrix(this_var) ~ c4a_expression + 
                        interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                      data = datalist[[j]], na.action = na.omit, family = "binomial")  
    my.model <- glm(as.matrix(this_var) ~ c4a_expression + c4b_expression + 
                        interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                      data = datalist[[j]], na.action = na.omit, family = "binomial")  
    p1 <- anova(my.model.0, my.model, test = "Chisq")
    p2 <- anova(my.model.1, my.model, test = "Chisq")
    df.logistic <- rbind(df.logistic, data.frame(data = names(datalist)[j],
                               ID = colnames(datalist[[j]])[i], 
                               N = nobs(my.model),
                               beta_C4A = summary(my.model)$coefficients[2, 1],
                               beta_C4B = summary(my.model)$coefficients[3, 1],
                               stderr_C4A = summary(my.model)$coefficients[2, 2],
                               stderr_C4B = summary(my.model)$coefficients[3, 2],
                               P_C4A = p1[2, 5],
                               P_C4B = p2[2, 5]))
    }

    
# Psychosis Gamma log-link
df.psychosis.gamma <- data.frame() 
  for (i in c(2499:2500)) { 
    this_var = datalist[[j]][, i]
    my.model.0 <- glm(as.matrix(this_var) ~ c4b_expression + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    my.model.1 <- glm(as.matrix(this_var) ~ c4a_expression + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    my.model <- glm(as.matrix(this_var) ~ c4a_expression + c4b_expression + 
                      interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                    data = datalist[[j]], na.action = na.omit, family = Gamma(link = "log"))
    p1 <- anova(my.model.0, my.model, test = "F")
    p2 <- anova(my.model.1, my.model, test = "F")
    df.psychosis.gamma <- rbind(df.psychosis.gamma, data.frame(data = names(datalist)[j],
                               ID = colnames(datalist[[j]])[i], 
                               N = nobs(my.model),
                               beta_C4A = summary(my.model)$coefficients[2, 1],
                               beta_C4B = summary(my.model)$coefficients[3, 1],
                               stderr_C4A = summary(my.model)$coefficients[2, 2],
                               stderr_C4B = summary(my.model)$coefficients[3, 2],
                               P_C4A = p1[2, 6],
                               P_C4B = p2[2, 6]))
 
  }

# Psychosis Logistic
df.psychosis.logistic <- data.frame() 
    my.model.0 <- glm(Psychosis_wPQ_susp ~ c4b_expression  + 
                        interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                      data = datalist[[j]], na.action = na.omit, family = "binomial")  
    my.model.1 <- glm(Psychosis_wPQ_susp ~ c4a_expression + 
                        interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                      data = datalist[[j]], na.action = na.omit, family = "binomial")  
    my.model <- glm(Psychosis_wPQ_susp ~ c4a_expression  + c4b_expression  + 
                        interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + site_id_l, 
                      data = datalist[[j]], na.action = na.omit, family = "binomial")  
    p1 <- anova(my.model.0, my.model, test = "Chisq")
    p2 <- anova(my.model.1, my.model, test = "Chisq")
    df.psychosis.logistic <- rbind(df.psychosis.logistic, data.frame(data = names(datalist)[j],
                               ID = "Psychosis_wPQ_susp", 
                               N = nobs(my.model),
                               beta_C4A = summary(my.model)$coefficients[2, 1],
                               beta_C4B = summary(my.model)$coefficients[3, 1],
                               stderr_C4A = summary(my.model)$coefficients[2, 2],
                               stderr_C4B = summary(my.model)$coefficients[3, 2],
                               P_C4A = p1[2, 5],
                               P_C4B = p2[2, 5]))


df.sex <- rbind(df.linear, df.gamma1)
df.sex <- rbind(df.sex, df.gamma2)
df.sex <- rbind(df.sex, df.logistic)
df.sex <- rbind(df.sex, df.psychosis.gamma)
df.sex <- rbind(df.sex, df.psychosis.logistic)
df.sex$FDR_C4A <- p.adjust(df.sex$P_C4A,'fdr')
df.sex$FDR_C4B <- p.adjust(df.sex$P_C4B,'fdr')
df.sex$Category <- ifelse(df.sex$ID %in% c("nihtbx_picvocab_fc", "nihtbx_flanker_fc", "nihtbx_list_fc", "nihtbx_cardsort_fc", "nihtbx_pattern_fc", "nihtbx_picture_fc", "nihtbx_reading_fc", "nihtbx_fluidcomp_fc", "nihtbx_cryst_fc", "nihtbx_totalcomp_fc", "lmt_scr_perc_correct", "pea_wiscv_tss"), "Cognition", ifelse(df.sex$ID %in% c("anthro_waist_cm", "anthroheightcalc", "anthroweightcalc"), "Anthropometrics", ifelse(df.sex$ID %in% c("bis_y_ss_bas_drive", "bis_y_ss_bas_fs", "bis_y_ss_bas_fs", "bis_y_ss_bas_rr", "bis_y_ss_basm_drive", "bis_y_ss_basm_rr", "bis_y_ss_bism_sum"), "BIS/BAS", ifelse(df.sex$ID %in% c("bpm_t_scr_attention_t", "bpm_t_scr_external_t", "bpm_t_scr_internal_t", "bpm_t_scr_totalprob_t"), "BRIEF",ifelse(df.sex$ID %in% c("cbcl_scr_07_ocd_t", "cbcl_scr_07_sct_t", "cbcl_scr_07_stress_t", "cbcl_scr_dsm5_adhd_t", "cbcl_scr_dsm5_anxdisord_t", "cbcl_scr_dsm5_conduct_t", "cbcl_scr_dsm5_depress_t", "cbcl_scr_dsm5_opposit_t", "cbcl_scr_dsm5_somaticpr_t", "cbcl_scr_syn_aggressive_t", "cbcl_scr_syn_anxdep_t", "cbcl_scr_syn_attention_t", "cbcl_scr_syn_external_t", "cbcl_scr_syn_internal_t", "cbcl_scr_syn_rulebreak_t", "cbcl_scr_syn_social_t", "cbcl_scr_syn_somatic_t", "cbcl_scr_syn_thought_t", "cbcl_scr_syn_totprob_t", "cbcl_scr_syn_withdep_t"), "CBCL", ifelse(df.sex$ID %in% c("devhx_16_p", "devhx_20_p", "devhx_21_p"), "Dev History", ifelse(df.sex$ID %in% c("fes_p_ss_fc_pr_p", "fes_y_ss_fc_pr", "latent_factor_ss_general_ses", "latent_factor_ss_perinatal", "latent_factor_ss_social", "srpf_y_ss_iiss", "stq_y_ss_weekday", "stq_y_ss_weekend"), "Environment", ifelse(df.sex$ID %in% c("hormone_scr_dhea_mean", "hormone_scr_ert_mean", "pds_p_ss_all_category_2", "hormone_scr_hse_mean"), "Hormones/Puberty", ifelse(df.sex$ID %in% c("ksads_1_842_p", "ksads_1_842_t", "ksads_1_847_p", "ksads_1_847_t", "ksads_10_869_p", "ksads_10_870_p", "ksads_10_914_p", "ksads_10_914_t", "ksads_11_917_p", "ksads_11_918_p", "ksads_11_919_p", "ksads_11_920_p", "ksads_14_853_p", "ksads_14_854_p", "ksads_14_855_p", "ksads_15_901_p", "ksads_15_902_p", "ksads_16_897_p", "ksads_16_899_p", "ksads_18_903_p", "ksads_2_833_p", "ksads_2_833_t", "ksads_2_837_p", "ksads_2_837_t", "ksads_2_839_p", "ksads_2_839_t", "ksads_23_945_p", "ksads_23_945_t", "ksads_23_946_t", "ksads_23_947_p", "ksads_23_947_t", "ksads_23_956_p", "ksads_23_956_t", "ksads_23_957_p", "ksads_23_957_t", "ksads_23_958_p", "ksads_23_958_t", "ksads_23_959_t", "ksads_4_829_p", "ksads_4_849_p", "ksads_7_862_p", "ksads_7_910_p", "ksads_8_863_p", "ksads_8_864_p", "ksads_8_912_p", "ksads_8_912_t", "ksads_9_867_p", "ksads_9_868_p"), "KSADS", ifelse(df.sex$ID %in% c("medhx_ss_4b_p", "medhx_ss_5b_p", "medhx_ss_6a_times_p", "medhx_ss_6b_times_p", "medhx_ss_6c_times_p", "medhx_ss_6d_times_p", "medhx_ss_6e_times_p", "medhx_ss_6f_times_p", "medhx_ss_6g_times_p", "medhx_ss_6h_times_p", "medhx_ss_6i_times_p", "medhx_ss_6j_times_p", "medhx_ss_6k_times_p", "medhx_ss_6l_times_p", "medhx_ss_6m_times_p", "medhx_ss_6n_times_p", "medhx_ss_6o_times_p", "medhx_ss_6p_times_p", "medhx_ss_6q_times_p", "medhx_ss_6s_times_p", "medhx_ss_9b_p"), "Medical History", ifelse(df.sex$ID %in% c("pgbi_p_ss_score", "upps_y_ss_lack_of_perseverance", "upps_y_ss_lack_of_planning", "upps_y_ss_negative_urgency", "upps_y_ss_positive_urgency", "upps_y_ss_sensation_seeking"), "Implusivity", ifelse(df.sex$ID %in% c("psb_p_ss_mean", "psb_y_ss_mean", "resiliency5a_y_p", "resiliency5b_y_p", "resiliency6a_y_p", "resiliency6b_y_p", "ssrs_p_ss_sum"), "Social Behavior", ifelse(df.sex$ID %in% c("sds_p_ss_da", "sds_p_ss_dims", "sds_p_ss_does", "sds_p_ss_sbd", "sds_p_ss_shy", "sds_p_ss_swtd", "sds_p_ss_total"), "Sleep", ifelse(df.sex$ID %in% c("pps_y_ss_number_plus1", "pps_y_ss_severity_score_plus1", "Psychosis_wPQ_susp"), "Psychosis", 0))))))))))))))

print(df.sex)

df.sex$Direction <- ifelse(df.sex$beta_C4A >= 0, "Positive", "Negative")

plot <- ggplot(df.sex, aes(x=Category, y=-log10(P_C4A), shape=Direction)) + 
  geom_point(aes(col=Category, size=abs(beta_C4A), fill=Category)) + 
  scale_shape_manual(values=c(25,24)) +
  theme_classic() + 
  theme(axis.text.x = element_blank(), axis.ticks=element_blank()) + 
  labs(color="Category", size="Abs. Beta", x="Phenotypes", y="-log10(P)") + 
  geom_text_repel(data=. %>% 
                    mutate(label = ifelse(P_C4A < 0.05, as.character(ID), "")),
                  aes(label=label),
                  size=3,
                  box.padding = 1,
                  force = 1,
                  force_pull = 1,
                  min.segment.length = 0,
                  point.padding = 0,
                  direction = "both",
                  segment.linetype = 6,
                  segment.color = "gray",
                  segment.curvature = -1e-20,
                  arrow = arrow(length = unit(0.015, "npc")),
                  max.overlaps = Inf
  ) + 
  geom_hline(yintercept=-log10(0.05), color="red", size=1, alpha=0.3, linetype="dashed") +
  ggtitle("C4A PheWAS")
print(plot + ylim(0, 5))
}
```

## Graph Psychosis-C4A results #
```{r}
data <- data.frame(
  name=c("ALL","AFR","Latinx","EUR","FEMALE","MALE",
         "ALL","AFR","Latinx","EUR","FEMALE","MALE",
         "ALL","AFR","Latinx","EUR","FEMALE","MALE") ,  
  value=c(0.00867,-0.036,0.129,0.004,0.032,-0.009,
          0.0040,-0.042,0.150,0.005,0.049,-0.027,
          0.0940,-0.112, 0.302, 0.073, 0.313, -0.057),
  se=c(0.04037248, 0.1136, 0.0995, 0.0487, 0.0597, 0.0546,
       0.0600, 0.1730, 0.1422, 0.0727, 0.0877, 0.0816,
       0.1592, 0.4238, 0.3543, 0.2011, 0.2481, 0.2102),
  measure=c("PQ-B Number", "PQ-B Number", "PQ-B Number", "PQ-B Number", "PQ-B Number", "PQ-B Number",
            "PQ-B Severity","PQ-B Severity", "PQ-B Severity", "PQ-B Severity", "PQ-B Severity", "PQ-B Severity",
            "Case/Control","Case/Control", "Case/Control", "Case/Control", "Case/Control", "Case/Control")
  )

# Barplot
my.plot <- data  %>% mutate(name = fct_relevel(name, "MALE", "FEMALE", "EUR", "Latinx", "AFR", "ALL")) %>%
  ggplot(aes(x=name, y=value)) + 
  geom_bar(stat = "identity", alpha=0.7, aes (fill = name)) +
  geom_errorbar(aes(ymin=value-se, ymax=value+se), width=.2,position=position_dodge(.9),size=0.25) +
  labs(x="Group", y = "Beta") +
  theme_classic() +
  coord_flip() +
  ylim(-0.7, 0.7) +
  geom_hline(yintercept = 0)
print(my.plot + facet_grid(. ~ measure))

brewer.pal(n = 11, name = "RdYlBu")
brewer.pal(n = 9, name = "Greys")
brewer.pal(n = 9, name = "Purples")

my.plot1 <- my.plot + scale_fill_manual(values = c("#969696", "#525252", "mediumpurple4", "mediumorchid4", "mediumorchid3","darkorchid1")) + facet_grid(. ~ measure) + theme(legend.position = "none") # save 3 x 11
my.plot1
ggsave(my.plot1, file = '../results/Figure2_Bar_PLEbeta.Ancestry.Sex.pdf', device = cairo_pdf, width = 11, height=3, units = 'in')
```

