---
title: "06_GREx.Brain"
output:
  html_document:
    df_print: paged
---

## Install packages #
```{r}
rm(list = ls())
options(stringsAsFactors = FALSE)

library(tidyverse)
library(lme4)
library(ggseg)
library(ggseg3d)
library(sjPlot)
library(plotrix)
library(ggridges)
library(ggpubr)
library(rstatix)
theme_set(theme_minimal())
```

## Save the subcortical regions #
```{r}
my.plot <- ggseg(atlas=aseg, mapping=aes(fill=region), show.legend = F) 
my.plot
ggsave(my.plot, file = '../results/Figure1_BrainAtlas_Subcortical.pdf', device = cairo_pdf, width = 5, height=4, units = 'in')
```
  
## Load data #
```{r}
load("ABCD.Release.3.0.C4.Merged.Data.PhewasVars.Rda")
```

## Average across left and right hemispheres #
```{r}
varlist <- c("smri_thick_cdk_bankssts", "smri_thick_cdk_cdacate", "smri_thick_cdk_cdmdfr", "smri_thick_cdk_cuneus", "smri_thick_cdk_ehinal", "smri_thick_cdk_fusiform", "smri_thick_cdk_ifpl", "smri_thick_cdk_iftm", "smri_thick_cdk_ihcate", "smri_thick_cdk_locc", "smri_thick_cdk_lobfr", "smri_thick_cdk_lingual", "smri_thick_cdk_mobfr", "smri_thick_cdk_mdtm", "smri_thick_cdk_parahpal", "smri_thick_cdk_paracn", "smri_thick_cdk_parsopc", "smri_thick_cdk_parsobis", "smri_thick_cdk_parstgris", "smri_thick_cdk_pericc", "smri_thick_cdk_postcn", "smri_thick_cdk_ptcate", "smri_thick_cdk_precn", "smri_thick_cdk_pc", "smri_thick_cdk_rracate", "smri_thick_cdk_rrmdfr", "smri_thick_cdk_sufr", "smri_thick_cdk_supl", "smri_thick_cdk_sutm", "smri_thick_cdk_sm", "smri_thick_cdk_frpole", "smri_thick_cdk_tmpole", "smri_thick_cdk_trvtm", "smri_thick_cdk_insula", "smri_area_cdk_bankssts", "smri_area_cdk_cdacate", "smri_area_cdk_cdmdfr", "smri_area_cdk_cuneus", "smri_area_cdk_ehinal", "smri_area_cdk_fusiform", "smri_area_cdk_ifpl", "smri_area_cdk_iftm", "smri_area_cdk_ihcate", "smri_area_cdk_locc", "smri_area_cdk_lobfr", "smri_area_cdk_lingual", "smri_area_cdk_mobfr", "smri_area_cdk_mdtm", "smri_area_cdk_parahpal", "smri_area_cdk_paracn", "smri_area_cdk_parsopc", "smri_area_cdk_parsobis", "smri_area_cdk_parstgris", "smri_area_cdk_pericc", "smri_area_cdk_postcn", "smri_area_cdk_ptcate", "smri_area_cdk_precn", "smri_area_cdk_pc", "smri_area_cdk_rracate", "smri_area_cdk_rrmdfr", "smri_area_cdk_sufr", "smri_area_cdk_supl", "smri_area_cdk_sutm", "smri_area_cdk_sm", "smri_area_cdk_frpole", "smri_area_cdk_tmpole", "smri_area_cdk_trvtm", "smri_area_cdk_insula", "smri_vol_scs_cbwmatter", "smri_vol_scs_ltventricle", "smri_vol_scs_inflatvent", "smri_vol_scs_crbwmatter", "smri_vol_scs_crbcortex", "smri_vol_scs_tp", "smri_vol_scs_caudate", "smri_vol_scs_putamen", "smri_vol_scs_pallidum", "smri_vol_scs_hpus", "smri_vol_scs_amygdala", "smri_vol_scs_vedc")

for (i in 1:length(varlist)){
  abcdData[, paste(varlist[[i]])] <- rowMeans(abcdData[,c(paste0(varlist[[i]], "rh"), paste0(varlist[[i]], "lh"))], na.rm=TRUE)
}

# NaN to NA
is.nan.data.frame <- function(x)
  do.call(cbind, lapply(x, is.nan))
abcdData[is.nan(abcdData)] <- NA
```

## Filter data #
```{r}
abcdData_baseline <- abcdData %>% filter(eventname == "baseline_year_1_arm_1")
abcdData_baseline %>% group_by(ethnicity) %>% tally() 

abcdData_baseline_C4 <- abcdData_baseline %>% filter(!is.na(c4a_total))
abcdData_baseline_C4 %>% group_by(ethnicity) %>% tally() 

abcdData_baseline_C4_filtered <- abcdData_baseline_C4 %>% filter(ethnicity %in% c("AFR", "AMR", "EUR"))
abcdData_baseline_C4_filtered %>% group_by(ethnicity) %>% tally() 

abcdData_baseline_C4_filtered <- abcdData_baseline_C4_filtered %>%
  filter(c4_allele1_structure %in% c("AL","AL-AL","AL-BL", "AL-BS", "BS"))
abcdData_baseline_C4_filtered <- abcdData_baseline_C4_filtered %>%
  filter(c4_allele2_structure %in% c("AL","AL-AL","AL-BL", "AL-BS", "BS"))

abcdData_baseline_C4_filtered %>% group_by(rel_family_id) %>% tally() %>% arrange(desc(n))  
```

## Update labels #
```{r}
abcdData_baseline_C4_filtered$ethnicity <- as.factor(abcdData_baseline_C4_filtered$ethnicity)
levels(abcdData_baseline_C4_filtered$ethnicity)
levels(abcdData_baseline_C4_filtered$ethnicity) <- list (Latinx = "AMR", EUR = "EUR", AFR = "AFR")
levels(abcdData_baseline_C4_filtered$ethnicity)
```

## Group by ancestry and sex #
```{r}
afr <- filter(abcdData_baseline_C4_filtered, ethnicity == "AFR")
latinx <- filter(abcdData_baseline_C4_filtered, ethnicity == "Latinx")
eur <- filter(abcdData_baseline_C4_filtered, ethnicity == "EUR")

male <- filter(abcdData_baseline_C4_filtered, sex == "M")
female <- filter(abcdData_baseline_C4_filtered, sex == "F")
```

## WBV, surface area, cortical thickness #
```{r}
which(colnames(abcdData_baseline_C4_filtered) == "smri_vol_scs_wholeb")  # 569
which(colnames(abcdData_baseline_C4_filtered) == "mrisdp_453")  # 570
which(colnames(abcdData_baseline_C4_filtered) == "mrisdp_151")  # 571

# Association by ancestry
datalist <- list(abcdData_baseline_C4_filtered, afr, latinx, eur)
names(datalist) <- c("abcdData_baseline_C4_filtered", "afr", "latinx", "eur")

for (j in 1:length(datalist)) {
  df <- data.frame() 
  print(names(datalist)[j])
  for (i in 569:571) {
    this_var = datalist[[j]][, i]
    mod0 <- lmer(as.matrix(this_var) ~ c4b_expression + 
                   interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex +
                   (1 | mri_info_deviceserialnumber) + (1|rel_family_id),
                 data = datalist[[j]], REML = FALSE)
    mod1 <- lmer(as.matrix(this_var) ~ c4a_expression + 
                   interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex +
                   (1 | mri_info_deviceserialnumber) + (1|rel_family_id),
                 data = datalist[[j]], REML = FALSE)
    mod2 <- lmer(as.matrix(this_var) ~ c4a_expression + c4b_expression + 
                   interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex +
                   (1 | mri_info_deviceserialnumber) + (1|rel_family_id),
                 data = datalist[[j]], REML = FALSE)
    p1 <- anova(mod0, mod2)
    p2 <- anova(mod1, mod2)
    df <- rbind(df, data.frame(data = names(datalist)[j],
                               ID = colnames(datalist[[j]])[i], 
                               N = nobs(mod2),
                               beta_C4A = summary(mod2)$coefficients[2, 1],
                               beta_C4B = summary(mod2)$coefficients[3, 1],
                               stderr_C4A = summary(mod2)$coefficients[2, 2],
                               stderr_C4B = summary(mod2)$coefficients[3, 2],
                               P_C4A = p1[2, 8],
                               P_C4B = p2[2, 8]))
  }
    df$fdr_C4A = p.adjust(df$P_C4A,'fdr')
    df$fdr_C4B = p.adjust(df$P_C4B,'fdr')
    print(df)
}

# Association by sex
datalist <- list(female, male)
names(datalist) <- c("female", "male")

for (j in 1:length(datalist)) {
  df <- data.frame() 
  print(names(datalist)[j])
  for (i in 569:571) {
    this_var = datalist[[j]][, i]
    mod0 <- lmer(as.matrix(this_var) ~ c4b_expression + 
                   interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + 
                   + (1 | mri_info_deviceserialnumber) + (1|rel_family_id),
                 data = datalist[[j]], REML = FALSE)
    mod1 <- lmer(as.matrix(this_var) ~ c4a_expression + 
                   interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + 
                   + (1 | mri_info_deviceserialnumber) + (1|rel_family_id),
                 data = datalist[[j]], REML = FALSE)
    mod2 <- lmer(as.matrix(this_var) ~ c4a_expression + c4b_expression + 
                   interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + 
                   + (1 | mri_info_deviceserialnumber) + (1|rel_family_id),
                 data = datalist[[j]], REML = FALSE)
    p1 <- anova(mod0, mod2)
    p2 <- anova(mod1, mod2)
    df <- rbind(df, data.frame(data = names(datalist)[j],
                               ID = colnames(datalist[[j]])[i], 
                               N = nobs(mod2),
                               beta_C4A = summary(mod2)$coefficients[2, 1],
                               beta_C4B = summary(mod2)$coefficients[3, 1],
                               stderr_C4A = summary(mod2)$coefficients[2, 2],
                               stderr_C4B = summary(mod2)$coefficients[3, 2],
                               P_C4A = p1[2, 8],
                               P_C4B = p2[2, 8]))
  }
    df$fdr_C4A = p.adjust(df$P_C4A,'fdr')
    df$fdr_C4B = p.adjust(df$P_C4B,'fdr')
    print(df)
}
```

## WBV, surface area, cortical thickness - sex interaction #
```{r}
which(colnames(abcdData_baseline_C4_filtered) == "smri_vol_scs_wholeb")  # 569
which(colnames(abcdData_baseline_C4_filtered) == "mrisdp_453")  # 570
which(colnames(abcdData_baseline_C4_filtered) == "mrisdp_151")  # 571

# Association by ancestry
datalist <- list(abcdData_baseline_C4_filtered)
names(datalist) <- c("abcdData_baseline_C4_filtered")

for (j in 1:length(datalist)) {
  df <- data.frame() 
  print(names(datalist)[j])
  for (i in 569:571) {
    this_var = datalist[[j]][, i]
    mod0 <- lmer(as.matrix(this_var) ~ c4a_expression + c4b_expression * sex + 
                   interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + 
                   (1 | mri_info_deviceserialnumber) + (1|rel_family_id),
                 data = datalist[[j]], REML = FALSE)
    mod1 <- lmer(as.matrix(this_var) ~ c4b_expression + c4a_expression * sex + 
                   interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + 
                   (1 | mri_info_deviceserialnumber) + (1|rel_family_id),
                 data = datalist[[j]], REML = FALSE)
    mod2 <- lmer(as.matrix(this_var) ~ c4a_expression * sex + c4b_expression * sex +
                   interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + 
                   (1 | mri_info_deviceserialnumber) + (1|rel_family_id),
                 data = datalist[[j]], REML = FALSE)
    p1 <- anova(mod0, mod2)
    p2 <- anova(mod1, mod2)
    df <- rbind(df, data.frame(data = names(datalist)[j],
                               ID = colnames(datalist[[j]])[i], 
                               N = nobs(mod2),
                               beta_C4A = summary(mod2)$coefficients[11, 1],
                               beta_C4B = summary(mod2)$coefficients[12, 1],
                               stderr_C4A = summary(mod2)$coefficients[11, 2],
                               stderr_C4B = summary(mod2)$coefficients[12, 2],
                               P_C4A = p1[2, 8],
                               P_C4B = p2[2, 8]))
  }
    df$fdr_C4A = p.adjust(df$P_C4A,'fdr')
    df$fdr_C4B = p.adjust(df$P_C4B,'fdr')
    print(df)
}
```

## Cortical thickness - All #
```{r}
bl <- colorRampPalette(c("navy","royalblue","lightskyblue"))(200)                       
re <- colorRampPalette(c("mistyrose", "red2","darkred"))(200)
trans <- yarrr::transparent("blue", trans.val = 1)

which(colnames(abcdData_baseline_C4_filtered) == "smri_thick_cdk_bankssts") #2557
which(colnames(abcdData_baseline_C4_filtered) == "smri_thick_cdk_insula") #2590

# Association - multiethnic cohort
datalist <- list(abcdData_baseline_C4_filtered)
names(datalist) <- c("abcdData_baseline_C4_filtered")

for (j in 1:length(datalist)) {
  df <- data.frame() 
  print(names(datalist)[j])
  for (i in 2557:2590) {
    this_var = datalist[[j]][, i]
    mod0 <- lmer(as.matrix(this_var) ~ c4b_expression + 
                   interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + mrisdp_151 +
                   (1 | mri_info_deviceserialnumber) + (1|rel_family_id),
                 data = datalist[[j]], REML = FALSE)
    mod1 <- lmer(as.matrix(this_var) ~ c4a_expression + 
                   interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + mrisdp_151 +
                   (1 | mri_info_deviceserialnumber) + (1|rel_family_id),
                 data = datalist[[j]], REML = FALSE)
    mod2 <- lmer(as.matrix(this_var) ~ c4a_expression + c4b_expression + 
                   interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + mrisdp_151 +
                   (1 | mri_info_deviceserialnumber) + (1|rel_family_id),
                 data = datalist[[j]], REML = FALSE)
    p1 <- anova(mod0, mod2)
    p2 <- anova(mod1, mod2)
    df <- rbind(df, data.frame(data = names(datalist)[j],
                               ID = colnames(datalist[[j]])[i], 
                               N = nobs(mod2),
                               beta_C4A = summary(mod2)$coefficients[2, 1],
                               beta_C4B = summary(mod2)$coefficients[3, 1],
                               stderr_C4A = summary(mod2)$coefficients[2, 2],
                               stderr_C4B = summary(mod2)$coefficients[3, 2],
                               P_C4A = p1[2, 8],
                               P_C4B = p2[2, 8]))
    
  }
  
df$fdr_C4A = p.adjust(df$P_C4A,'fdr')
df$fdr_C4B = p.adjust(df$P_C4B,'fdr')
print(df)
}
```

## Surface area - All #
```{r}
bl <- colorRampPalette(c("navy","royalblue","lightskyblue"))(200)                       
re <- colorRampPalette(c("mistyrose", "red2","darkred"))(200)
trans <- yarrr::transparent("blue", trans.val = 1)

which(colnames(abcdData_baseline_C4_filtered) == "smri_area_cdk_bankssts") #2591
which(colnames(abcdData_baseline_C4_filtered) == "smri_area_cdk_insula") #2624

# Association - multiethnic cohort
datalist <- list(abcdData_baseline_C4_filtered)
names(datalist) <- c("abcdData_baseline_C4_filtered")

for (j in 1:length(datalist)) {
  df <- data.frame() 
  print(names(datalist)[j])
  for (i in 2591:2624) {
    this_var = datalist[[j]][, i]
    mod0 <- lmer(as.matrix(this_var) ~ c4b_expression + 
                   interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + mrisdp_453 +
                   (1 | mri_info_deviceserialnumber) + (1|rel_family_id),
                 data = datalist[[j]], REML = FALSE)
    mod1 <- lmer(as.matrix(this_var) ~ c4a_expression + 
                   interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + mrisdp_453 +
                   (1 | mri_info_deviceserialnumber) + (1|rel_family_id),
                 data = datalist[[j]], REML = FALSE)
    mod2 <- lmer(as.matrix(this_var) ~ c4a_expression + c4b_expression + 
                   interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + mrisdp_453 +
                   (1 | mri_info_deviceserialnumber) + (1|rel_family_id),
                 data = datalist[[j]], REML = FALSE)
    p1 <- anova(mod0, mod2)
    p2 <- anova(mod1, mod2)
    df <- rbind(df, data.frame(data = names(datalist)[j],
                               ID = colnames(datalist[[j]])[i], 
                               N = nobs(mod2),
                               beta_C4A = summary(mod2)$coefficients[2, 1],
                               beta_C4B = summary(mod2)$coefficients[3, 1],
                               stderr_C4A = summary(mod2)$coefficients[2, 2],
                               stderr_C4B = summary(mod2)$coefficients[3, 2],
                               P_C4A = p1[2, 8],
                               P_C4B = p2[2, 8]))
  }

df$fdr_C4A = p.adjust(df$P_C4A,'fdr')
df$fdr_C4B = p.adjust(df$P_C4B,'fdr')
print(df)
}
```

## Plot sex interaction #
```{r}
sjplot_pal(pal = "breakfast club")

interaction.mod <- lmer(smri_area_cdk_ehinal ~ c4a_expression*sex + c4b_expression*sex + 
                   interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + mrisdp_453 +
                   (1 | mri_info_deviceserialnumber) + (1|rel_family_id),
                 data = abcdData_baseline_C4_filtered, REML = FALSE)
my.plot <- plot_model(interaction.mod, type = "pred", terms = c("c4a_expression", "sex"), colors = c("springgreen4", "slateblue1"))
my.plot1 <- my.plot + labs(x="Predicted C4A Expression", y = "Entorhinal Cortex Surface Area (mm2)", fill = "Sex") + 
  ggtitle("") +
  theme_classic() 
ggsave(my.plot1, file = '../results/Figure3_Regression_C4A.Entorhinal.Sex.pdf', device = cairo_pdf, width = 5, height=3, units = 'in')
```

## Volume - All #
```{r}
bl <- colorRampPalette(c("navy","royalblue","lightskyblue"))(200)                       
re <- colorRampPalette(c("mistyrose", "red2","darkred"))(200)
trans <- yarrr::transparent("blue", trans.val = 1)

which(colnames(abcdData_baseline_C4_filtered) == "smri_vol_scs_cbwmatter") #2625
which(colnames(abcdData_baseline_C4_filtered) == "smri_vol_scs_pallidum") #2633
which(colnames(abcdData_baseline_C4_filtered) == "smri_vol_scs_3rdventricle") #543
which(colnames(abcdData_baseline_C4_filtered) == "smri_vol_scs_bstem") #545
which(colnames(abcdData_baseline_C4_filtered) == "smri_vol_scs_hpus") #2634
which(colnames(abcdData_baseline_C4_filtered) == "smri_vol_scs_amygdala") #2635
which(colnames(abcdData_baseline_C4_filtered) == "smri_vol_scs_csf") #548
which(colnames(abcdData_baseline_C4_filtered) == "smri_vol_scs_aal") #549
which(colnames(abcdData_baseline_C4_filtered) == "smri_vol_scs_vedc") #2636
which(colnames(abcdData_baseline_C4_filtered) == "smri_vol_scs_ccps") #564
which(colnames(abcdData_baseline_C4_filtered) == "smri_vol_scs_ccat") #568

# Association - multiethnic cohort
datalist <- list(abcdData_baseline_C4_filtered)
names(datalist) <- c("abcdData_baseline_C4_filtered")

for (j in 1:length(datalist)) {
  df <- data.frame() 
  print(names(datalist)[j])
  for (i in c(2625:2633, 543:545, 2634:2635, 548:549, 2636, 564:568)) {
    this_var = datalist[[j]][, i]
    mod0 <- lmer(as.matrix(this_var) ~ c4b_expression + 
                   interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + smri_vol_scs_wholeb +
                   (1 | mri_info_deviceserialnumber) + (1|rel_family_id),
                 data = datalist[[j]], REML = FALSE)
    mod1 <- lmer(as.matrix(this_var) ~ c4a_expression + 
                   interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + smri_vol_scs_wholeb +
                   (1 | mri_info_deviceserialnumber) + (1|rel_family_id),
                 data = datalist[[j]], REML = FALSE)
    mod2 <- lmer(as.matrix(this_var) ~ c4a_expression + c4b_expression + 
                   interview_age + ses_AvgIncomeParentEdu + pc1 + pc2 + pc3 + pc4 + sex + smri_vol_scs_wholeb +
                   (1 | mri_info_deviceserialnumber) + (1|rel_family_id),
                 data = datalist[[j]], REML = FALSE)
    p1 <- anova(mod0, mod2)
    p2 <- anova(mod1, mod2)
    df <- rbind(df, data.frame(data = names(datalist)[j],
                               ID = colnames(datalist[[j]])[i], 
                               N = nobs(mod2),
                               beta_C4A = summary(mod2)$coefficients[2, 1],
                               beta_C4B = summary(mod2)$coefficients[3, 1],
                               stderr_C4A = summary(mod2)$coefficients[2, 2],
                               stderr_C4B = summary(mod2)$coefficients[3, 2],
                               P_C4A = p1[2, 8],
                               P_C4B = p2[2, 8]))
  }

df$fdr_C4A = p.adjust(df$P_C4A,'fdr')
df$fdr_C4B = p.adjust(df$P_C4B,'fdr')
print(df)
}
```

## Get longitudinal data #  
```{r}
## Year 1
abcdData_Y1 <- abcdData %>% filter(eventname == "1_year_follow_up_y_arm_1")
abcdData_Y1 %>% group_by(ethnicity) %>% tally() 

abcdData_Y1_C4 <- abcdData_Y1 %>% filter(!is.na(c4a_total))
abcdData_Y1_C4 %>% group_by(ethnicity) %>% tally() 

abcdData_Y1_C4_filtered <- abcdData_Y1_C4 %>% filter(ethnicity %in% c("AFR", "AMR", "EUR"))
abcdData_Y1_C4_filtered %>% group_by(ethnicity) %>% tally() 

abcdData_Y1_C4_filtered <- abcdData_Y1_C4_filtered %>%
  filter(c4_allele1_structure %in% c("AL","AL-AL","AL-BL", "AL-BS", "BS"))
abcdData_Y1_C4_filtered <- abcdData_Y1_C4_filtered %>%
  filter(c4_allele2_structure %in% c("AL","AL-AL","AL-BL", "AL-BS", "BS"))

abcdData_Y1_C4_filtered %>% group_by(rel_family_id) %>% tally() %>% arrange(desc(n)) 

afr.Y1 <- filter(abcdData_Y1_C4_filtered, ethnicity == "AFR")
amr.Y1 <- filter(abcdData_Y1_C4_filtered, ethnicity == "AMR")
eur.Y1 <- filter(abcdData_Y1_C4_filtered, ethnicity == "EUR")

male.Y1 <- filter(abcdData_Y1_C4_filtered, sex == "M")
female.Y1 <- filter(abcdData_Y1_C4_filtered, sex == "F")


## Year 2
abcdData_Y2 <- abcdData %>% filter(eventname == "2_year_follow_up_y_arm_1")
abcdData_Y2 %>% group_by(ethnicity) %>% tally() 

abcdData_Y2_C4 <- abcdData_Y2 %>% filter(!is.na(c4a_total))
abcdData_Y2_C4 %>% group_by(ethnicity) %>% tally() 

abcdData_Y2_C4_filtered <- abcdData_Y2_C4 %>% filter(ethnicity %in% c("AFR", "AMR", "EUR"))
abcdData_Y2_C4_filtered %>% group_by(ethnicity) %>% tally() 

abcdData_Y2_C4_filtered <- abcdData_Y2_C4_filtered %>%
  filter(c4_allele1_structure %in% c("AL","AL-AL","AL-BL", "AL-BS", "BS"))
abcdData_Y2_C4_filtered <- abcdData_Y2_C4_filtered %>%
  filter(c4_allele2_structure %in% c("AL","AL-AL","AL-BL", "AL-BS", "BS"))

abcdData_Y2_C4_filtered %>% group_by(rel_family_id) %>% tally() %>% arrange(desc(n))  

afr.Y2 <- filter(abcdData_Y2_C4_filtered, ethnicity == "AFR")
amr.Y2 <- filter(abcdData_Y2_C4_filtered, ethnicity == "AMR")
eur.Y2 <- filter(abcdData_Y2_C4_filtered, ethnicity == "EUR")

male.Y2 <- filter(abcdData_Y2_C4_filtered, sex == "M")
female.Y2 <- filter(abcdData_Y2_C4_filtered, sex == "F")
```

## Get baseline  smri_area_cdk_ehinal  to add to longitudinal #
```{r}
## Baseline brain data
abcdData_baseline_C4_filtered_brain <- dplyr::select(abcdData_baseline_C4_filtered, subjectkey, smri_area_cdk_ehinal, interview_age, mrisdp_453)

abcdData_baseline_C4_filtered_brain$smri_area_cdk_ehinal_baseline <- abcdData_baseline_C4_filtered_brain$smri_area_cdk_ehinal
abcdData_baseline_C4_filtered_brain$interview_age_baseline <- abcdData_baseline_C4_filtered_brain$interview_age
abcdData_baseline_C4_filtered_brain$mrisdp_453_baseline <- abcdData_baseline_C4_filtered_brain$mrisdp_453

abcdData_baseline_C4_filtered_brain <- dplyr::select(abcdData_baseline_C4_filtered_brain, subjectkey, smri_area_cdk_ehinal_baseline, interview_age_baseline, mrisdp_453_baseline)

male <- merge(male, abcdData_baseline_C4_filtered_brain, by = 'subjectkey')
female <- merge(female, abcdData_baseline_C4_filtered_brain, by = 'subjectkey')

abcdData_Y1_C4_filtered <- merge(abcdData_Y1_C4_filtered, abcdData_baseline_C4_filtered_brain, by = 'subjectkey')
afr.Y1 <- merge(afr.Y1, abcdData_baseline_C4_filtered_brain, by = 'subjectkey')
amr.Y1 <- merge(amr.Y1, abcdData_baseline_C4_filtered_brain, by = 'subjectkey')
eur.Y1 <- merge(eur.Y1, abcdData_baseline_C4_filtered_brain, by = 'subjectkey')
male.Y1 <- merge(male.Y1, abcdData_baseline_C4_filtered_brain, by = 'subjectkey')
female.Y1 <- merge(female.Y1, abcdData_baseline_C4_filtered_brain, by = 'subjectkey')


abcdData_Y2_C4_filtered <- merge(abcdData_Y2_C4_filtered, abcdData_baseline_C4_filtered_brain, by = 'subjectkey')
afr.Y2 <- merge(afr.Y2, abcdData_baseline_C4_filtered_brain, by = 'subjectkey')
amr.Y2 <- merge(amr.Y2, abcdData_baseline_C4_filtered_brain, by = 'subjectkey')
eur.Y2 <- merge(eur.Y2, abcdData_baseline_C4_filtered_brain, by = 'subjectkey')
male.Y2 <- merge(male.Y2, abcdData_baseline_C4_filtered_brain, by = 'subjectkey')
female.Y2 <- merge(female.Y2, abcdData_baseline_C4_filtered_brain, by = 'subjectkey')
```
  
## Plot baseline ENT SA #
```{r}
my.plot <- ggplot(abcdData_baseline_C4_filtered, aes(x = smri_area_cdk_ehinal, y = sex)) + 
  stat_density_ridges(quantile_lines = TRUE, quantiles = c(0.25, 0.75), scale = 0.9, aes(fill = sex), alpha = 0.6) +
  scale_fill_manual(values = c("springgreen4","slateblue1")) +
  labs(x="Entorhinal Cortex SA at Baseline", y="Sex") +
  theme(legend.position = "none") +
  scale_y_discrete(expand = c(0, 0)) +
  scale_x_continuous(expand = c(0, 0))
my.plot1 <- my.plot + coord_flip() # save 10 x 3
ggsave(my.plot1, file = '../results/Figure3_Distribution_Entorhinal.Baseline.Sex.pdf', device = cairo_pdf, width = 3, height=10, units = 'in')
```

## 1-Year Follow-up - ENT SA #
```{r}
## Year 1 follow-up

# Male
quantile(male.Y1$smri_area_cdk_ehinal_baseline, na.rm = TRUE) #Small.25%=363.0, Large75%=464.0
nrow(male.Y1[male.Y1$smri_area_cdk_ehinal_baseline>=464.0, ]) 
nrow(male.Y1[male.Y1$smri_area_cdk_ehinal_baseline<=363.0, ]) 

BigBrain <- subset(male.Y1, smri_area_cdk_ehinal_baseline>=464.0)
BigBrain$Size <- "Top 25%"
  
SmallBrain <- subset(male.Y1, smri_area_cdk_ehinal_baseline<=363.0)
SmallBrain$Size <- "Bottom 25%"

mean <- mean(BigBrain$pps_y_ss_number, na.rm=TRUE)
sd <- sd(BigBrain$pps_y_ss_number, na.rm=TRUE)
se <- std.error(BigBrain$pps_y_ss_number, na.rm=TRUE)
wilcox <- wilcox.test(BigBrain$pps_y_ss_number, SmallBrain$pps_y_ss_number, conf.int = TRUE, conf.level = 0.95)
p <- wilcox$p.value
wilcox$conf.int
big.df.male.number <- data.frame(mean, se, p)
big.df.male.number$Sex <- "Male"
big.df.male.number$Size <- "Top 25%"
big.df.male.number$Variable <- "Number of Events"

mean <- mean(SmallBrain$pps_y_ss_number, na.rm=TRUE)
sd <- sd(SmallBrain$pps_y_ss_number, na.rm=TRUE)
se <- std.error(SmallBrain$pps_y_ss_number, na.rm=TRUE)
wilcox <- wilcox.test(BigBrain$pps_y_ss_number, SmallBrain$pps_y_ss_number, conf.int = TRUE, conf.level = 0.95)
p <- wilcox$p.value
wilcox$conf.int
small.df.male.number <- data.frame(mean, se, p)
small.df.male.number$Sex <- "Male"
small.df.male.number$Size <- "Bottom 25%"
small.df.male.number$Variable <- "Number of Events"

mean <- mean(BigBrain$pps_y_ss_severity_score, na.rm=TRUE)
sd <- sd(BigBrain$pps_y_ss_severity_score, na.rm=TRUE)
se <- std.error(BigBrain$pps_y_ss_severity_score, na.rm=TRUE)
wilcox <- wilcox.test(BigBrain$pps_y_ss_severity_score, SmallBrain$pps_y_ss_severity_score, conf.int = TRUE, conf.level = 0.95)
p <- wilcox$p.value
wilcox$conf.int
big.df.male.severity <- data.frame(mean, se, p)
big.df.male.severity$Sex <- "Male"
big.df.male.severity$Size <- "Top 25%"
big.df.male.severity$Variable <- "Severity of Events"

mean <- mean(SmallBrain$pps_y_ss_severity_score, na.rm=TRUE)
sd <- sd(SmallBrain$pps_y_ss_severity_score, na.rm=TRUE)
se <- std.error(SmallBrain$pps_y_ss_severity_score, na.rm=TRUE)
wilcox <- wilcox.test(BigBrain$pps_y_ss_severity_score, SmallBrain$pps_y_ss_severity_score, conf.int = TRUE, conf.level = 0.95)
p <- wilcox$p.value
small.df.male.severity <- data.frame(mean, se, p)
small.df.male.severity$Sex <- "Male"
small.df.male.severity$Size <- "Bottom 25%"
small.df.male.severity$Variable <- "Severity of Events"

df.male.number <- rbind(big.df.male.number, small.df.male.number)
df.male.severity <- rbind(big.df.male.severity, small.df.male.severity)
df.male.big.small <- rbind (BigBrain, SmallBrain)

male.iqr.number <- df.male.big.small %>%
  group_by(Size) %>%
  get_summary_stats(pps_y_ss_number, type = "median_iqr") 
print(male.iqr.number)

male.test.number <- df.male.big.small %>% 
  wilcox_test(pps_y_ss_number ~ Size) %>%
  add_significance()
print(male.test.number)

print(df.male.big.small %>% wilcox_effsize(pps_y_ss_number ~ Size))

male.iqr.severity <- df.male.big.small %>%
  group_by(Size) %>%
  get_summary_stats(pps_y_ss_severity_score, type = "median_iqr")
print(male.iqr.severity)

male.test.severity <- df.male.big.small %>% 
  wilcox_test(pps_y_ss_severity_score ~ Size) %>%
  add_significance()
print(male.test.severity)

print(df.male.big.small %>% wilcox_effsize(pps_y_ss_severity_score ~ Size))

# Female
quantile(female.Y1$smri_area_cdk_ehinal_baseline, na.rm = TRUE) #Small.25%=321.0 , Large75%=408.0
nrow(female.Y1[female.Y1$smri_area_cdk_ehinal_baseline>=408.0, ]) 
nrow(female.Y1[female.Y1$smri_area_cdk_ehinal_baseline<=321.0 , ]) 

BigBrain <- subset(female.Y1, smri_area_cdk_ehinal_baseline>=408.0)
BigBrain$Size <- "Top 25%"
  
SmallBrain <- subset(female.Y1, smri_area_cdk_ehinal_baseline<=321.0 )
SmallBrain$Size <- "Bottom 25%"

mean <- mean(BigBrain$pps_y_ss_number, na.rm=TRUE)
sd <- sd(BigBrain$pps_y_ss_number, na.rm=TRUE)
se <- std.error(BigBrain$pps_y_ss_number, na.rm=TRUE)
wilcox <- wilcox.test(BigBrain$pps_y_ss_number, SmallBrain$pps_y_ss_number, conf.int = TRUE, conf.level = 0.95)
p <- wilcox$p.value
big.df.female.number <- data.frame(mean, se, p)
big.df.female.number$Sex <- "Female"
big.df.female.number$Size <- "Top 25%"
big.df.female.number$Variable <- "Number of Events"

mean <- mean(SmallBrain$pps_y_ss_number, na.rm=TRUE)
sd <- sd(SmallBrain$pps_y_ss_number, na.rm=TRUE)
se <- std.error(SmallBrain$pps_y_ss_number, na.rm=TRUE)
wilcox <- wilcox.test(BigBrain$pps_y_ss_number, SmallBrain$pps_y_ss_number, conf.int = TRUE, conf.level = 0.95)
p <- wilcox$p.value
small.df.female.number <- data.frame(mean, se, p)
small.df.female.number$Sex <- "Female"
small.df.female.number$Size <- "Bottom 25%"
small.df.female.number$Variable <- "Number of Events"

mean <- mean(BigBrain$pps_y_ss_severity_score, na.rm=TRUE)
sd <- sd(BigBrain$pps_y_ss_severity_score, na.rm=TRUE)
se <- std.error(BigBrain$pps_y_ss_severity_score, na.rm=TRUE)
wilcox <- wilcox.test(BigBrain$pps_y_ss_severity_score, SmallBrain$pps_y_ss_severity_score, conf.int = TRUE, conf.level = 0.95)
p <- wilcox$p.value
big.df.female.severity <- data.frame(mean, se, p)
big.df.female.severity$Sex <- "Female"
big.df.female.severity$Size <- "Top 25%"
big.df.female.severity$Variable <- "Severity of Events"

mean <- mean(SmallBrain$pps_y_ss_severity_score, na.rm=TRUE)
sd <- sd(SmallBrain$pps_y_ss_severity_score, na.rm=TRUE)
se <- std.error(SmallBrain$pps_y_ss_severity_score, na.rm=TRUE)
wilcox <- wilcox.test(BigBrain$pps_y_ss_severity_score, SmallBrain$pps_y_ss_severity_score, conf.int = TRUE, conf.level = 0.95)
p <- wilcox$p.value
small.df.female.severity <- data.frame(mean, se, p)
small.df.female.severity$Sex <- "Female"
small.df.female.severity$Size <- "Bottom 25%"
small.df.female.severity$Variable <- "Severity of Events"

df.female.number <- rbind(big.df.female.number, small.df.female.number)
df.female.severity <- rbind(big.df.female.severity, small.df.female.severity)
df.female.big.small <- rbind (BigBrain, SmallBrain)

female.iqr.number <- df.female.big.small %>%
  group_by(Size) %>%
  get_summary_stats(pps_y_ss_number, type = "median_iqr") 
print(female.iqr.number)

female.test.number <- df.female.big.small %>% 
  wilcox_test(pps_y_ss_number ~ Size) %>%
  add_significance()
print(female.test.number)

print(df.female.big.small %>% wilcox_effsize(pps_y_ss_number ~ Size))

female.iqr.severity <- df.female.big.small %>%
  group_by(Size) %>%
  get_summary_stats(pps_y_ss_severity_score, type = "median_iqr")
print(female.iqr.severity)

female.test.severity <- df.female.big.small %>% 
  wilcox_test(pps_y_ss_severity_score ~ Size) %>%
  add_significance()
print(female.test.severity)

print(df.female.big.small %>% wilcox_effsize(pps_y_ss_severity_score ~ Size))

# Combine
df.number <- rbind(df.male.number, df.female.number)
df.severity <- rbind(df.male.severity, df.female.severity)
df.year1 <- rbind(df.number, df.severity)
```

## 2-Year Follow-up - ENT SA #
```{r}
## Year 2 follow-up

# Male
quantile(male.Y2$smri_area_cdk_ehinal_baseline, na.rm = TRUE) #Small.25%=363.0, Large75%=464.75
nrow(male.Y2[male.Y2$smri_area_cdk_ehinal_baseline>=464.75, ]) 
nrow(male.Y2[male.Y2$smri_area_cdk_ehinal_baseline<=363.0, ]) 

BigBrain <- subset(male.Y2, smri_area_cdk_ehinal_baseline>=464.75)
BigBrain$Size <- "Top 25%"
  
SmallBrain <- subset(male.Y2, smri_area_cdk_ehinal_baseline<=363.0)
SmallBrain$Size <- "Bottom 25%"

mean <- mean(BigBrain$pps_y_ss_number, na.rm=TRUE)
sd <- sd(BigBrain$pps_y_ss_number, na.rm=TRUE)
se <- std.error(BigBrain$pps_y_ss_number, na.rm=TRUE)
wilcox <- wilcox.test(BigBrain$pps_y_ss_number, SmallBrain$pps_y_ss_number)
p <- wilcox$p.value
big.df.male.number <- data.frame(mean, se, p)
big.df.male.number$Sex <- "Male"
big.df.male.number$Size <- "Top 25%"
big.df.male.number$Variable <- "Number of Events"

mean <- mean(SmallBrain$pps_y_ss_number, na.rm=TRUE)
sd <- sd(SmallBrain$pps_y_ss_number, na.rm=TRUE)
se <- std.error(SmallBrain$pps_y_ss_number, na.rm=TRUE)
wilcox <- wilcox.test(BigBrain$pps_y_ss_number, SmallBrain$pps_y_ss_number)
p <- wilcox$p.value
small.df.male.number <- data.frame(mean, se, p)
small.df.male.number$Sex <- "Male"
small.df.male.number$Size <- "Bottom 25%"
small.df.male.number$Variable <- "Number of Events"

mean <- mean(BigBrain$pps_y_ss_severity_score, na.rm=TRUE)
sd <- sd(BigBrain$pps_y_ss_severity_score, na.rm=TRUE)
se <- std.error(BigBrain$pps_y_ss_severity_score, na.rm=TRUE)
wilcox <- wilcox.test(BigBrain$pps_y_ss_severity_score, SmallBrain$pps_y_ss_severity_score)
p <- wilcox$p.value
big.df.male.severity <- data.frame(mean, se, p)
big.df.male.severity$Sex <- "Male"
big.df.male.severity$Size <- "Top 25%"
big.df.male.severity$Variable <- "Severity of Events"

mean <- mean(SmallBrain$pps_y_ss_severity_score, na.rm=TRUE)
sd <- sd(SmallBrain$pps_y_ss_severity_score, na.rm=TRUE)
se <- std.error(SmallBrain$pps_y_ss_severity_score, na.rm=TRUE)
wilcox <- wilcox.test(BigBrain$pps_y_ss_severity_score, SmallBrain$pps_y_ss_severity_score)
p <- wilcox$p.value
small.df.male.severity <- data.frame(mean, se, p)
small.df.male.severity$Sex <- "Male"
small.df.male.severity$Size <- "Bottom 25%"
small.df.male.severity$Variable <- "Severity of Events"

df.male.number <- rbind(big.df.male.number, small.df.male.number)
df.male.severity <- rbind(big.df.male.severity, small.df.male.severity)
df.male.big.small <- rbind (BigBrain, SmallBrain)

male.iqr.number <- df.male.big.small %>%
  group_by(Size) %>%
  get_summary_stats(pps_y_ss_number, type = "median_iqr") 
print(male.iqr.number)

male.test.number <- df.male.big.small %>% 
  wilcox_test(pps_y_ss_number ~ Size) %>%
  add_significance()
print(male.test.number)

print(df.male.big.small %>% wilcox_effsize(pps_y_ss_number ~ Size))

male.iqr.severity <- df.male.big.small %>%
  group_by(Size) %>%
  get_summary_stats(pps_y_ss_severity_score, type = "median_iqr")
print(male.iqr.severity)

male.test.severity <- df.male.big.small %>% 
  wilcox_test(pps_y_ss_severity_score ~ Size) %>%
  add_significance()
print(male.test.severity)

print(df.male.big.small %>% wilcox_effsize(pps_y_ss_severity_score ~ Size))


# Female
quantile(female.Y2$smri_area_cdk_ehinal_baseline, na.rm = TRUE) #Small.25%=320.500 , Large75%=408.625
nrow(female.Y2[female.Y2$smri_area_cdk_ehinal_baseline>=408.625, ]) 
nrow(female.Y2[female.Y2$smri_area_cdk_ehinal_baseline<=320.500 , ]) 

BigBrain <- subset(female.Y2, smri_area_cdk_ehinal_baseline>=408.625)
BigBrain$Size <- "Top 25%"
  
SmallBrain <- subset(female.Y2, smri_area_cdk_ehinal_baseline<=320.500 )
SmallBrain$Size <- "Bottom 25%"

mean <- mean(BigBrain$pps_y_ss_number, na.rm=TRUE)
sd <- sd(BigBrain$pps_y_ss_number, na.rm=TRUE)
se <- std.error(BigBrain$pps_y_ss_number, na.rm=TRUE)
wilcox <- wilcox.test(BigBrain$pps_y_ss_number, SmallBrain$pps_y_ss_number)
p <- wilcox$p.value
big.df.female.number <- data.frame(mean, se, p)
big.df.female.number$Sex <- "Female"
big.df.female.number$Size <- "Top 25%"
big.df.female.number$Variable <- "Number of Events"

mean <- mean(SmallBrain$pps_y_ss_number, na.rm=TRUE)
sd <- sd(SmallBrain$pps_y_ss_number, na.rm=TRUE)
se <- std.error(SmallBrain$pps_y_ss_number, na.rm=TRUE)
wilcox <- wilcox.test(BigBrain$pps_y_ss_number, SmallBrain$pps_y_ss_number)
p <- wilcox$p.value
small.df.female.number <- data.frame(mean, se, p)
small.df.female.number$Sex <- "Female"
small.df.female.number$Size <- "Bottom 25%"
small.df.female.number$Variable <- "Number of Events"

mean <- mean(BigBrain$pps_y_ss_severity_score, na.rm=TRUE)
sd <- sd(BigBrain$pps_y_ss_severity_score, na.rm=TRUE)
se <- std.error(BigBrain$pps_y_ss_severity_score, na.rm=TRUE)
wilcox <- wilcox.test(BigBrain$pps_y_ss_severity_score, SmallBrain$pps_y_ss_severity_score)
p <- wilcox$p.value
big.df.female.severity <- data.frame(mean, se, p)
big.df.female.severity$Sex <- "Female"
big.df.female.severity$Size <- "Top 25%"
big.df.female.severity$Variable <- "Severity of Events"

mean <- mean(SmallBrain$pps_y_ss_severity_score, na.rm=TRUE)
sd <- sd(SmallBrain$pps_y_ss_severity_score, na.rm=TRUE)
se <- std.error(SmallBrain$pps_y_ss_severity_score, na.rm=TRUE)
wilcox <- wilcox.test(BigBrain$pps_y_ss_severity_score, SmallBrain$pps_y_ss_severity_score)
p <- wilcox$p.value
small.df.female.severity <- data.frame(mean, se, p)
small.df.female.severity$Sex <- "Female"
small.df.female.severity$Size <- "Bottom 25%"
small.df.female.severity$Variable <- "Severity of Events"

df.female.number <- rbind(big.df.female.number, small.df.female.number)
df.female.severity <- rbind(big.df.female.severity, small.df.female.severity)
df.female.big.small <- rbind (BigBrain, SmallBrain)

female.iqr.number <- df.female.big.small %>%
  group_by(Size) %>%
  get_summary_stats(pps_y_ss_number, type = "median_iqr") 
print(female.iqr.number)

female.test.number <- df.female.big.small %>% 
  wilcox_test(pps_y_ss_number ~ Size) %>%
  add_significance()
print(female.test.number)

print(df.female.big.small %>% wilcox_effsize(pps_y_ss_number ~ Size))

female.iqr.severity <- df.female.big.small %>%
  group_by(Size) %>%
  get_summary_stats(pps_y_ss_severity_score, type = "median_iqr")
print(female.iqr.severity)

female.test.severity <- df.female.big.small %>% 
  wilcox_test(pps_y_ss_severity_score ~ Size) %>%
  add_significance()
print(female.test.severity)

print(df.female.big.small %>% wilcox_effsize(pps_y_ss_severity_score ~ Size))

# Combine
df.number <- rbind(df.male.number, df.female.number)
df.severity <- rbind(df.male.severity, df.female.severity)
df.year2 <- rbind(df.number, df.severity)
```

## Plot by year #
```{r}
df.year1$year <- "1-Year Follow-Up"
df.year2$year <- "2-Year Follow-Up"
df.year1.year2 <- rbind(df.year1, df.year2)
df.number.of.events <- df.year1.year2[c(1:4, 9:12),]
df.severity.of.events <- df.year1.year2[c(5:8, 13:16),]

# Plot 
my.plot <- ggplot(df.number.of.events, aes(x=Size, y=mean, fill=Size)) + 
  scale_y_continuous(breaks = c(0, 1, 2)) +
  geom_bar(stat="identity", color="black", position=position_dodge()) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2,position=position_dodge(.9)) 
my.plot1 <- my.plot + theme_classic() + labs(x="Baseline Entorhinal Cortex Surface Area", y = "Psychosis Symptoms", fill = "SA Quartile") +
  scale_fill_manual(values=c('#999999','white')) + facet_grid(Sex~year) +
  geom_text(aes(label = format(mean, digits = 2), y = 0.7)) + theme(legend.position="left")
my.plot1
ggsave(my.plot1, file = '../results/Figure3_Bar_PLEnumber.Entorhinal.Sex.pdf', device = cairo_pdf, width = 6.5, height=3.5, units = 'in')

my.plot <- ggplot(df.severity.of.events, aes(x=Size, y=mean, fill=Size)) + 
  geom_bar(stat="identity", color="black", position=position_dodge()) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2,position=position_dodge(.9)) 
my.plot1 <- my.plot + theme_classic() + labs(x="Baseline Entorhinal Cortex Surface Area", y = "Psychosis Symptoms", fill = "SA Quartile") +
  scale_fill_manual(values=c('#999999','white')) + facet_grid(Sex~year) +
  geom_text(aes(label = format(mean, digits = 2), y = 0.7)) + theme(legend.position="left")
my.plot1
ggsave(my.plot1, file = '../results/Figure3_Bar_PLEseverity.Entorhinal.Sex.pdf', device = cairo_pdf, width = 6.5, height=3.5, units = 'in')
```
